---
title: "Pilot analyses: version 3"
output: 
  github_document:
    toc: true
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---

this is a notebook dedicated to probing the "crossover" effect observed at the end of `pilot_analysis.md`

```{r load packages, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(tidyverse)
library(patchwork)
library(lme4)
library(lmerTest)
library(emmeans)

# potentially useful in the future
library(performance) # for easy model comparisons
# library(jtools) # for alternative model summaries
library(sjPlot) # for formatting model result tables
# library(MetBrewer) # for pretty art-inspired color palettes
```

```{r plotting setup: colors, outdir, functions, include=F}
# define plotting colors 
colors <- c('incongruent' = "#F8766D", 'neutral' = "#00BA38", 'congruent'="#619CFF")
trialCong_cols <- c('incongruent' = "#F8766D", 'equal evidence' = "lemonchiffon3", 'congruent'="#619CFF")
cueType_cols <- c('50%' = 'gray', '80%' = 'darkblue')
blues <- RColorBrewer::brewer.pal(9, "Blues")[c(4,5,6,7,8)]
cueCong_colors <- c('0.8 cue: incongruent vizEv' = "#F8766D", 
            '0.8 cue: equal vizEv' = "#00BA38", 
            '0.8 cue: congruent vizEv'="#619CFF",
            '0.5 cue: imgA vizEv' = 'purple',
            '0.5 cue: imgB vizEv' = 'orange',
            '0.5 cue: equal vizEv' = '#00BA38')

# where to save plots
outdir <- 'pilot_analysis_figs/'

# function for plotting effects of continuous predictors
varRange <- function(df, xVar, precision=1) {
  return(seq(min(df[,xVar], na.rm=T),
             max(df[,xVar], na.rm=T),
             precision))
}
```

```{r load & tidy inference data, include=FALSE}
evidence_frames <- read.csv('../data/tidied/evidenceFrames.csv')  %>% rename(respFrame = response_frame)
inference_files = list.files('../data', full.names = TRUE, pattern='block1_inference.csv', recursive = TRUE)
inference_keep_idx <- grep('excluded', inference_files, invert=T)
inference_df = do.call(rbind, lapply(inference_files[inference_keep_idx], function(x) { read.csv(x, header = TRUE)} )) 

############### tidy inference data ############### 
inferenceData <- inference_df %>%
  filter(subID != 16) %>%
  rename(trueTarget = targetIdx) %>% 
  select(-c(noise1frames, noise2frames, signal1frames, block, targetImg, cue_rgb, cue_string)) %>%
  full_join(., evidence_frames, by=c('subID', 'trial', 'catch_trial', 'congruent', 'respFrame', 'response')) %>%
  mutate(subID = factor(subID),
         congruent = factor(as.character(congruent), levels=c("0", "NaN", "1"), labels=c('incongruent', 'neutral', 'congruent')),
         respFrame = ifelse(is.na(respFrame), 540, respFrame),
         cueIdx = case_when(trueTarget == 1 & congruent == 'congruent' ~ 1,
                            trueTarget == 1 & congruent == 'incongruent' ~ 2,
                            trueTarget == 1 & congruent == 'incongruent' ~ 2,
                            trueTarget == 2 & congruent =='congruent' ~ 2,
                            trueTarget == 2 & congruent=='incongruent' ~ 1,
                            congruent == 'neutral' ~ 3),
         cueType = ifelse(cueIdx==3, '50% cue', '80% cue'),
         totalNoise = noise1frames_behav + noise2frames_behav,
         totalTarget1 = rowSums(across(c(signal1_target1, signal2_target1)), na.rm=T),
         totalTarget2 = rowSums(across(c(signal1_target2, signal2_target2)), na.rm=T),
         trialTarget = case_when(totalTarget1 > totalTarget2 ~ 1,
                                 totalTarget1 < totalTarget2 ~ 2,
                                 totalTarget1 == totalTarget2 ~ NA),
         # trialCongruence = case_when(cueIdx == trialTarget ~ 'congruent',
         #                             cueIdx != trialTarget ~ 'incongruent',
         #                             totalTarget1 == totalTarget2 ~ 'equal evidence'),
         # trialCongruence = factor(trialCongruence, levels=c('incongruent', 'equal evidence', 'congruent')),
         respPeriod = case_when(respFrame >= signal2Onset ~ 'signal2', 
                                respFrame >= noise2Onset & respFrame < signal2Onset ~ 'noise2',
                                respFrame > noise1frames_design & respFrame < noise2Onset ~ 'signal1',
                                respFrame < signal1Onset ~ 'noise1'), 
         cueCongChoice = case_when(cueIdx==3 ~ NA, cueIdx==response ~ 1, cueIdx!=response ~ 0),
         noise1_quartile = cut(noise1frames_behav, breaks=quantile(noise1frames_behav, na.rm=T), include.lowest = T, labels=F), 
         noise2_quartile = cut(noise2frames_behav, breaks=quantile(noise2frames_behav, na.rm=T), include.lowest = T, labels=F), 
         totalNoise_quartile = cut(totalNoise, breaks=quantile(totalNoise, na.rm=T), include.lowest = T, labels=F),
         catch_trial_cat = factor(catch_trial, levels=c(0,1), labels=c('test', 'catch'))) %>%
  group_by(subID) %>%
  mutate(logRT = log(RT),
         zlogRT = scale(logRT),
         zConf = scale(confResp),
         logConfRT = log(confRT),
         zlogconfRT = scale(logConfRT), 
         rt_quartile = cut(zlogRT, breaks=quantile(zlogRT, na.rm=T), include.lowest=T, labels=F),
         trial_quartile = cut(trial, breaks=quantile(trial), include.lowest=T, labels=F)) %>%
  ungroup()

rm(inference_files, inference_keep_idx, evidence_frames, inference_df)
```

```{r load & tidy model data, include=FALSE}
modelData <- read.csv('steadyState_modelBehavior.csv')

modelData <- modelData %>%
  mutate(congruent = case_when(cue==0.5 ~ NA,
                               congruent==0 ~ 'incongruent',
                               congruent==1 ~ 'congruent'),
         noise1frames_behav = case_when(RT > noise1Frames ~ noise1Frames,
                                         RT < noise1Frames ~ RT),
         noise2frames_behav = case_when(RT > signal2Onsets ~ noise2Frames,
                                         RT < signal2Onsets & RT > noise2Onsets ~ signal2Onsets - RT),
         signal1frames_behav = case_when(RT > signal1Onsets + signal1Frames ~ signal1Frames,
                                         RT < signal1Onsets + signal1Frames ~ noise2Onsets - RT),
         signal2frames_behav = case_when(RT < signal2Onsets ~ NA,
                                         RT > signal2Onsets ~ (signal2Onsets+signal2Frames)-RT),
         respPeriod = case_when(RT >= signal2Onsets ~ 'signal2', 
                                RT >= noise2Onsets & RT < signal2Onsets ~ 'noise2',
                                RT > noise1Frames & RT < noise2Onsets ~ 'signal1',
                                RT < signal1Onsets ~ 'noise1'),
         cueCongChoice = case_when(congruent == 'congruent' & forcedChoice == 1 ~ 1,
                                   congruent == 'incongruent' & forcedChoice == 1 ~ 1),
         noise1_quartile = cut(noise1frames_behav, breaks=quantile(noise1frames_behav, na.rm=T), include.lowest = T, labels=F), 
         noise2_quartile = cut(noise2frames_behav, breaks=quantile(noise2frames_behav, na.rm=T), include.lowest = T, labels=F)) %>% 
  group_by(subID) %>%
  mutate(logRT = log(RT),
         zlogRT = scale(logRT)) %>%
  ungroup()
```

```{r make dfs for analysis, include=FALSE}
inferenceData_tidy <- inferenceData %>%
  filter(is.na(response)==F) %>%
  mutate(cueType = factor(cueType),
         subID = factor(subID),
         resp1 = ifelse(response==1, 1, 0),
         resp2 = ifelse(response==1, 0, 1),
         respFinger = ifelse(resp1==1, '1', '2'),
         signal1_cueEv = case_when(cueIdx==1 ~ signal1_target1 - signal1_target2,
                                   cueIdx==2 ~ signal1_target2 - signal1_target1),
         # signal1_relEv = case_when(response==1 ~ signal1_target1 - signal1_target2,
         #                           response==2 ~ signal1_target2 - signal1_target1),
         # signal1_relEv_z = scale(signal1_relEv),
         # signal1_cueCong = case_when(cueIdx==1 & (signal1_target1 > signal1_target2) ~ '0.8 cue: congruent vizEv',
         #                             cueIdx==1 & (signal1_target1 < signal1_target2) ~ '0.8 cue: incongruent vizEv',
         #                             cueIdx==2 & (signal1_target1 > signal1_target2) ~ '0.8 cue: incongruent vizEv',
         #                             cueIdx==2 & (signal1_target1 < signal1_target2) ~ '0.8 cue: congruent vizEv',
         #                             cueIdx<3 & (signal1_target1 == signal1_target2) ~ '0.8 cue: equal vizEv',
         #                             cueIdx==3 & (signal1_target1 > signal1_target2) ~ '0.5 cue: imgA vizEv',
         #                             cueIdx==3 & (signal1_target1 < signal1_target2) ~ '0.5 cue: imgB vizEv',
         #                             cueIdx==3 & (signal1_target1 == signal1_target2) ~ '0.5 cue: equal vizEv'),
         # signal1_evCongChoice = case_when(signal1_target1 > signal1_target2 & response==1 ~ 1,
         #                                  signal1_target1 < signal1_target2 & response==2 ~ 1,
         #                                  signal1_target1 < signal1_target2 & response==1 ~ 0,
         #                                  signal1_target1 > signal1_target2 & response==2 ~ 0),
         # signal2_cueCong = case_when(cueIdx==1 & (signal2_target1 > signal2_target2) ~ '0.8 cue: congruent vizEv',
         #                             cueIdx==1 & (signal2_target1 < signal2_target2) ~ '0.8 cue: incongruent vizEv',
         #                             cueIdx==2 & (signal2_target1 > signal2_target2) ~ '0.8 cue: incongruent vizEv',
         #                             cueIdx==2 & (signal2_target1 < signal2_target2) ~ '0.8 cue: congruent vizEv',
         #                             cueIdx<3 & (signal2_target1 == signal2_target2) ~ '0.8 cue: equal vizEv',
         #                             cueIdx==3 & (signal2_target1 > signal2_target2) ~ '0.5 cue: imgA ev',
         #                             cueIdx==3 & (signal2_target1 < signal2_target2) ~ '0.5 cue: imgB ev',
         #                             cueIdx==3 & (signal2_target1 == signal2_target2) ~ '0.5 cue: equal ev'),
         # signal2_cueCong = factor(signal2_cueCong),
         # signal1_cueCong = factor(signal1_cueCong),
         noise1_seconds = noise1frames_behav * (1/60), 
         signal1RT = RT - noise1_seconds,
         vizLocked_respFrame = respFrame - noise1frames_behav,
         vizLocked_respFrame_t = vizLocked_respFrame / 60,
         vizLocked_sig2Resp = respFrame - (noise1frames_behav + signal1frames_behav + noise2frames_behav),
         vizLocked_sig2Resp = vizLocked_sig2Resp/60) %>% 
  group_by(subID) %>%
  mutate(zlog_sig1RT = log(signal1RT),
         zlog_sig1RT = scale(zlog_sig1RT))%>%
  ungroup()

modelData <- modelData %>% 
  mutate(cueType = factor(cue, levels=c(0.5, 0.8), labels=c('50% cue', '80% cue')),
         subID = factor(subID),
         noise1_seconds = noise1frames_behav * (1/60), 
         vizLocked_respFrame = RT - noise1frames_behav,
         vizLocked_respFrame_t = vizLocked_respFrame / 60,
         vizLocked_sig2Resp = RT - (noise1frames_behav + signal1frames_behav + noise2frames_behav),
         vizLocked_sig2Resp = vizLocked_sig2Resp/60) 
```

### original effect
```{r cueCongChoice_signal2 ~ noise2frames_behav * signal1Ev - continuous color: human, echo=F}

# make filtered df
df <- inferenceData_tidy %>%
    filter(catch_trial==0) %>%
    filter(respPeriod == 'signal2', cueIdx < 3) 

# fit model
hm <- glm(cueCongChoice ~ noise2frames_behav * signal1_cueEv, df, family = 'binomial')

# make vectors for plotting emmeans
plot_vals <- df %>%
  select(noise2frames_behav, signal1_cueEv) %>%
  summarise(noise_vals = quantile(noise2frames_behav, probs = seq(0,1,0.1), na.rm=T, names=F),
            signal_vals = quantile(signal1_cueEv, probs = seq(0,1,0.1), na.rm=T, names=F))

# compute expected marginal means
emm <- emmeans(hm, ~ noise2frames_behav | signal1_cueEv, type='response', 
               at = list(noise2frames_behav = plot_vals$noise_vals,
                      signal1_cueEv = plot_vals$signal_vals))

# save plot-formatted emmeans
emm_df <- emmip(hm, signal1_cueEv ~ noise2frames_behav, type='response', CIs=T, plotit=F,
                at = list(noise2frames_behav = plot_vals$noise_vals,
                      signal1_cueEv = plot_vals$signal_vals))

# plot emmeans over raw data
fullEffect <- df %>% 
  ggplot(aes(x=noise2frames_behav, y=cueCongChoice)) +
  theme_bw() + geom_hline(yintercept=0.5, linetype='dashed') + 
  scale_color_gradient2() + scale_fill_gradient2() + 
  geom_point(aes(color=signal1_cueEv), size=1.5, position=position_jitter(height=0.1)) + 
  # add emmeans
  geom_line(aes(xvar, yvar, color=signal1_cueEv, group=signal1_cueEv), emm_df, linewidth=1.5) +
  geom_pointrange(aes(xvar, yvar, ymin=UCL, ymax=LCL, color=signal1_cueEv, group=signal1_cueEv), emm_df) +
  labs(title = 'probability of choosing cue-congruent option during signal2', subtitle = '80% cues only')
```

A GLM where noise2 duration & signal1 evidence are permitted to interact returns a "marginally significant" main effect of signal1 evidence as well as a significant interaction:

```{r stats for human data, echo=F}

fullEffect
tab_model(hm, digits=4)

```

The generating model does not predict this crossover, nor does it return a main effect of signal1 evidence or an interaction:
```{r cueCongChoice_signal2 ~ noise2frames_behav * signal1Ev - continuous color: model, echo=F}
# filter data
m_df <- modelData %>% filter(respPeriod == 'signal2', cue==0.8)

# fit model
m <- glm(forcedChoice ~ noise2frames_behav * signal1_vizEv, m_df, family = 'binomial')

# make vectors for plotting emmeans
plot_vals <- m_df %>% 
  select(noise2frames_behav, signal1_vizEv) %>%
  summarise(noise_vals = quantile(noise2frames_behav, probs = seq(0,1,0.1), na.rm=T, names=F),
            signal_vals = quantile(signal1_vizEv, probs = seq(0,1,0.1), na.rm=T, names=F))

# compute expected marginal means
emm <- emmeans(m, ~ noise2frames_behav | signal1_vizEv, type='response', 
               at = list(noise2frames_behav = plot_vals$noise_vals,
                         signal1_vizEv = plot_vals$signal_vals))

# save plot-formatted emmeans
emm_df <- emmip(m, signal1_vizEv ~ noise2frames_behav, type='response', CIs=T, plotit=F,
                at = list(noise2frames_behav = plot_vals$noise_vals,
                         signal1_vizEv = plot_vals$signal_vals))

# plot emmeans over raw data
mp <- m_df %>% 
  ggplot(aes(x=noise2frames_behav, y=forcedChoice)) +
  theme_bw() + geom_hline(yintercept=0.5, linetype='dashed') + 
  scale_color_gradient2(low = 'forestgreen', high='purple4') + scale_fill_gradient2(low = 'forestgreen', high='purple4') + 
  geom_point(aes(color=signal1_vizEv), size=1.5, position=position_jitter(height=0.1)) + 
  # add emmeans
  geom_line(aes(xvar, yvar, color=signal1_vizEv, group=signal1_vizEv), emm_df, linewidth=0.5) +
  labs(title = 'model data', subtitle='signal2 responses on 80% cue trials only')
```

```{r stats for model data, echo=F}
mp
tab_model(m, digits=4)
```

If we don't allow an interaction between signal1 evidence and noise2 duration, the human data neither qualitatively nor quantitatively show an effect of signal1 evidence:
```{r cueCongChoice_signal2 ~ noise2frames_behav + signal1Ev - continuous color: human, echo=F}

hm <- glm(cueCongChoice ~ noise2frames_behav + signal1_cueEv, df, family = 'binomial')

# make vectors for plotting emmeans
plot_vals <- df %>%
  select(noise2frames_behav, signal1_cueEv) %>%
  summarise(noise_vals = quantile(noise2frames_behav, probs = seq(0,1,0.1), na.rm=T, names=F),
            signal_vals = quantile(signal1_cueEv, probs = seq(0,1,0.1), na.rm=T, names=F))

# compute expected marginal means
emm <- emmeans(hm, ~ noise2frames_behav | signal1_cueEv, type='response', 
               at = list(noise2frames_behav = plot_vals$noise_vals,
                      signal1_cueEv = plot_vals$signal_vals))

# save plot-formatted emmeans
emm_df <- emmip(hm, signal1_cueEv ~ noise2frames_behav, type='response', CIs=T, plotit=F,
                at = list(noise2frames_behav = plot_vals$noise_vals,
                      signal1_cueEv = plot_vals$signal_vals))

# plot emmeans over raw data
addEffect <- df %>% 
  ggplot(aes(x=noise2frames_behav, y=cueCongChoice)) +
  theme_bw() + geom_hline(yintercept=0.5, linetype='dashed') + 
  scale_color_gradient2() + scale_fill_gradient2() + 
  geom_point(aes(color=signal1_cueEv), size=1.5, position=position_jitter(height=0.1)) + 
  # add emmeans
  geom_line(aes(xvar, yvar, color=signal1_cueEv, group=signal1_cueEv), emm_df, linewidth=1.5) +
  geom_pointrange(aes(xvar, yvar, ymin=UCL, ymax=LCL, color=signal1_cueEv, group=signal1_cueEv), emm_df) +
  labs(title = 'probability of choosing cue-congruent option during signal2', subtitle = '80% cues only')
```

```{r plot and stats for additive model, echo=F}
addEffect
tab_model(hm, digits=4)
```

***

## first question: is this just an artifact of values at the extremes?
### i fit interaction models to noise2durations of varying lengths

```{r cueCongChoice_signal2: noise2 < 90, echo=F}
# make df
noise90_df <- df %>% filter(noise2frames_behav < 90)

# fit model
noise90 <- glm(cueCongChoice ~ noise2frames_behav * signal1_cueEv, noise90_df, family = 'binomial')

# make vectors for plotting emmeans
plot_vals <- noise90_df %>%
  select(noise2frames_behav, signal1_cueEv) %>%
  summarise(noise_vals = quantile(noise2frames_behav, probs = seq(0,1,0.1), na.rm=T, names=F),
            signal_vals = quantile(signal1_cueEv, probs = seq(0,1,0.1), na.rm=T, names=F))

# compute expected marginal means
emm <- emmeans(noise90, ~ noise2frames_behav | signal1_cueEv, type='response', 
               at = list(noise2frames_behav = plot_vals$noise_vals,
                      signal1_cueEv = plot_vals$signal_vals))

# save plot-formatted emmeans
emm_df <- emmip(noise90, signal1_cueEv ~ noise2frames_behav, type='response', CIs=T, plotit=F,
                at = list(noise2frames_behav = plot_vals$noise_vals,
                      signal1_cueEv = plot_vals$signal_vals))

# plot emmeans over raw data
noise90_effect <- noise90_df %>% 
  ggplot(aes(x=noise2frames_behav, y=cueCongChoice)) +
  theme_bw() + geom_hline(yintercept=0.5, linetype='dashed') + 
  scale_color_gradient2() + scale_fill_gradient2() + 
  geom_point(aes(color=signal1_cueEv), size=1.5, position=position_jitter(height=0.1)) + 
  # add emmeans
  geom_line(aes(xvar, yvar, color=signal1_cueEv, group=signal1_cueEv), emm_df, linewidth=1.5) +
  geom_pointrange(aes(xvar, yvar, ymin=UCL, ymax=LCL, color=signal1_cueEv, group=signal1_cueEv), emm_df) +
  labs(subtitle = '80% cues only: noise2frames < 90')
```

```{r cueCongChoice_signal2: noise2 < 120, echo=F}
# make df
noise120_df <- df %>% filter(noise2frames_behav < 120)

# fit model
noise120 <- glm(cueCongChoice ~ noise2frames_behav * signal1_cueEv, noise120_df, family = 'binomial')

# make vectors for plotting emmeans
plot_vals <- noise120_df %>%
  select(noise2frames_behav, signal1_cueEv) %>%
  summarise(noise_vals = quantile(noise2frames_behav, probs = seq(0,1,0.1), na.rm=T, names=F),
            signal_vals = quantile(signal1_cueEv, probs = seq(0,1,0.1), na.rm=T, names=F))

# compute expected marginal means
emm <- emmeans(noise120, ~ noise2frames_behav | signal1_cueEv, type='response', 
               at = list(noise2frames_behav = plot_vals$noise_vals,
                      signal1_cueEv = plot_vals$signal_vals))

# save plot-formatted emmeans
emm_df <- emmip(noise120, signal1_cueEv ~ noise2frames_behav, type='response', CIs=T, plotit=F,
                at = list(noise2frames_behav = plot_vals$noise_vals,
                      signal1_cueEv = plot_vals$signal_vals))

# plot emmeans over raw data
noise120_effect <- noise120_df %>% 
  ggplot(aes(x=noise2frames_behav, y=cueCongChoice)) +
  theme_bw() + geom_hline(yintercept=0.5, linetype='dashed') + 
  scale_color_gradient2() + scale_fill_gradient2() + 
  geom_point(aes(color=signal1_cueEv), size=1.5, position=position_jitter(height=0.1)) + 
  # add emmeans
  geom_line(aes(xvar, yvar, color=signal1_cueEv, group=signal1_cueEv), emm_df, linewidth=1.5) +
  geom_pointrange(aes(xvar, yvar, ymin=UCL, ymax=LCL, color=signal1_cueEv, group=signal1_cueEv), emm_df) +
  labs(subtitle = '80% cues only: noise2frames < 120')
```

```{r display plots, echo=F, fig.width=10}

noise90_effect + noise120_effect + fullEffect + plot_layout(guides = 'collect')

```

regression result tables for each plot in order:

```{r noise120 stats, echo=F}
tab_model(noise90, noise120, hm, digits=4,
          dv.labels = c('noise2frames < 90',
                        'noise2frames < 120', 
                        'all noise2frames'))
```

***

## next question: does the effect show up in RTs?

```{r vizLocked_sig2Resp ~ signal1_cueEv * noise2frames_behav: humans, echo=F}

# filter data
df <- inferenceData_tidy %>%
  filter(catch_trial == 0) %>%
  filter(respPeriod == 'signal2', cueIdx < 3)

# make vector for plotting emmeans
plot_vals <- df %>%
  select(noise2frames_behav, signal1_cueEv) %>%
  summarise(noise_vals = quantile(noise2frames_behav, probs = seq(0,1,0.1), na.rm=T, names=F),
            signal_vals = quantile(signal1_cueEv, probs = seq(0,1,0.1), na.rm=T, names=F))

# fit model
hm <- lm(vizLocked_sig2Resp ~ noise2frames_behav * signal1_cueEv, df)

# compute expected marginal means
emm <- emmeans(hm, ~ noise2frames_behav | signal1_cueEv, 
               at = list(noise2frames_behav = plot_vals$noise_vals,
                         signal1_cueEv = plot_vals$signal_vals))

# save plot-formatted emmeans
emm_df <- emmip(hm,  ~ noise2frames_behav | signal1_cueEv, CIs=T, plotit=F,
      at = list(noise2frames_behav = plot_vals$noise_vals,
                         signal1_cueEv = plot_vals$signal_vals))

# plot emmeans above raw data
hp <- df %>%
  ggplot(aes(x = noise2frames_behav, y = vizLocked_sig2Resp, group=signal1_cueEv)) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype='dashed') +
  geom_point(aes(color=signal1_cueEv), alpha=0.5, size=1) +
  geom_line(aes(x=xvar, y=yvar, group=signal1_cueEv, color=signal1_cueEv), data=emm_df, linewidth=1.5) +
  geom_pointrange(aes(xvar, yvar, ymin=UCL, ymax=LCL, color=signal1_cueEv, group=signal1_cueEv), emm_df) +
  labs(subtitle = 'signal2 RTs locked to onset of signal2 visual evidence', title = 'human data') +
  scale_color_gradient2() + scale_fill_gradient2() 
```

```{r vizLocked_sig2Resp ~ signal1_cueEv * noise2frames_behav: model, echo=F}

# filter data
m_df <- modelData %>%
    filter(respPeriod == 'signal2', cue==0.8)

# fit model
mm <- lm(vizLocked_sig2Resp ~ noise2frames_behav * signal1_vizEv, m_df)

# make vectors for plotting emmeans
plot_vals <- m_df %>%
  select(noise2frames_behav, signal1_vizEv) %>%
  summarise(noise_vals = quantile(noise2frames_behav, probs = seq(0,1,0.1), na.rm=T, names=F),
            signal_vals = quantile(signal1_vizEv, probs = seq(0,1,0.1), na.rm=T, names=F))

# compute expected marginal means
emm <- emmeans(mm, ~ noise2frames_behav | signal1_vizEv, 
               at = list(noise2frames_behav = plot_vals$noise_vals, 
                         signal1_vizEv = plot_vals$signal_vals))

# save plot-formatted emmeans
emm_df <- emmip(mm,  ~ noise2frames_behav | signal1_vizEv, CIs=T, plotit=F,
      at = list(noise2frames_behav = plot_vals$noise_vals, 
                         signal1_vizEv = plot_vals$signal_vals))

# plot emmeans above raw data
mp <- m_df %>%
  ggplot(aes(x=noise2frames_behav, y=vizLocked_sig2Resp)) +
  theme_bw() + geom_hline(yintercept=0.5, linetype='dashed') + 
  scale_color_gradient2() + scale_fill_gradient2() + 
  geom_point(aes(color=signal1_vizEv), size=1.5, position=position_jitter(height=0.1)) + 
  # add emmeans
  geom_line(aes(xvar, yvar, color=signal1_vizEv, group=signal1_vizEv), emm_df, linewidth=1.5) +
  geom_pointrange(aes(xvar, yvar, ymin=UCL, ymax=LCL, color=signal1_vizEv, group=signal1_vizEv), emm_df) +
  labs(title = 'model data', subtitle = 'signal2 RTs locked to onset of signal2 visual evidence')
```

```{r show plot and model stats, echo=F, fig.width=10}
hp + mp
tab_model(hm, mm,
          dv.labels = c('human results',
                        'model results'))
```

There is maybe a hint of the effect in RTs, but the model's predictions here make far more sense and actually return a main effect of noise2 duration. 

***

## last (for now) question: does the effect show up in confidence ratings?

```{r signal2conf ~ noise2frames_behav * signal1_cueEv, echo=F}
# filter data
df <- inferenceData_tidy %>%
    filter(catch_trial==0) %>% filter(respPeriod == 'signal2', cueIdx < 3)

# fit model
hm <- lm(zConf ~ noise2frames_behav * signal1_cueEv, df)

# make vector for plotting emmeans
plot_vals <- df %>%
  select(noise2frames_behav, signal1_cueEv) %>%
  summarise(noise_vals = quantile(noise2frames_behav, probs = seq(0,1,0.1), na.rm=T, names=F),
            signal_vals = quantile(signal1_cueEv, probs = seq(0,1,0.1), na.rm=T, names=F))

# compute expected marginal means
emm <- emmeans(hm, ~ noise2frames_behav | signal1_cueEv, 
               at = list(noise2frames_behav = plot_vals$noise_vals,
                         signal1_cueEv = plot_vals$signal_vals))

# save plot-formatted emmeans
emm_df <- emmip(hm, ~ noise2frames_behav | signal1_cueEv, CIs=T, plotit=F,
                at = list(signal1_cueEv = plot_vals$signal_vals,
                          noise2frames_behav = plot_vals$noise_vals))

# plot emmeans over raw data
hp <- df %>% 
  ggplot(aes(x=noise2frames_behav, y=zConf)) +
  theme_bw() + geom_hline(yintercept=0, linetype='dashed') + 
  scale_color_gradient2() + scale_fill_gradient2() + 
  geom_point(aes(color=signal1_cueEv), size=1.5, position=position_jitter(height=0.1)) + 
  # add emmeans
  geom_line(aes(xvar, yvar, color=signal1_cueEv, group=signal1_cueEv), emm_df, linewidth=0.5) +
  geom_pointrange(aes(xvar, yvar, ymin=LCL, ymax=UCL, color=signal1_cueEv), emm_df) + 
  labs(title = 'signal2 confidence', subtitle='all noise2frames')
```

```{r signal2conf: noise < 90, echo=F}
# filter data
df <- inferenceData_tidy %>% filter(catch_trial == 0, respPeriod == 'signal2', cueIdx < 3, noise2frames_behav < 90)

# fit model
hm90 <- lm(zConf ~ noise2frames_behav * signal1_cueEv, df)

# make vector for plotting emmeans
plot_vals <- df %>%
  select(noise2frames_behav, signal1_cueEv) %>%
  summarise(noise_vals = quantile(noise2frames_behav, probs = seq(0,1,0.1), na.rm=T, names=F),
            signal_vals = quantile(signal1_cueEv, probs = seq(0,1,0.1), na.rm=T, names=F))

# compute expected marginal means
emm <- emmeans(hm90, ~ noise2frames_behav | signal1_cueEv, 
               at = list(noise2frames_behav = plot_vals$noise_vals,
                         signal1_cueEv = plot_vals$signal_vals))

# save plot-formatted emmeans
emm_df <- emmip(hm90, ~ noise2frames_behav | signal1_cueEv, CIs=T, plotit=F,
                at = list(signal1_cueEv = plot_vals$signal_vals,
                          noise2frames_behav = plot_vals$noise_vals))

# plot emmeans over raw data
hp90 <- df %>% 
  ggplot(aes(x=noise2frames_behav, y=zConf)) +
  theme_bw() + geom_hline(yintercept=0, linetype='dashed') + 
  scale_color_gradient2() + scale_fill_gradient2() + 
  geom_point(aes(color=signal1_cueEv), size=1.5, position=position_jitter(height=0.1)) + 
  # add emmeans
  geom_line(aes(xvar, yvar, color=signal1_cueEv, group=signal1_cueEv), emm_df, linewidth=0.5) +
  geom_pointrange(aes(xvar, yvar, ymin=LCL, ymax=UCL, color=signal1_cueEv), emm_df) + 
  labs(title = 'signal2 confidence', subtitle='noise2frames < 90')
```

```{r signal2conf: noise < 120, echo=F}
# filter data
df <- inferenceData_tidy %>% filter(catch_trial == 0, respPeriod == 'signal2', cueIdx < 3, noise2frames_behav < 120)

# fit model
hm120 <- lm(zConf ~ noise2frames_behav * signal1_cueEv, df)

# make vector for plotting emmeans
plot_vals <- df %>%
  select(noise2frames_behav, signal1_cueEv) %>%
  summarise(noise_vals = quantile(noise2frames_behav, probs = seq(0,1,0.1), na.rm=T, names=F),
            signal_vals = quantile(signal1_cueEv, probs = seq(0,1,0.1), na.rm=T, names=F))

# compute expected marginal means
emm <- emmeans(hm120, ~ noise2frames_behav | signal1_cueEv, 
               at = list(noise2frames_behav = plot_vals$noise_vals,
                         signal1_cueEv = plot_vals$signal_vals))

# save plot-formatted emmeans
emm_df <- emmip(hm120, ~ noise2frames_behav | signal1_cueEv, CIs=T, plotit=F,
                at = list(signal1_cueEv = plot_vals$signal_vals,
                          noise2frames_behav = plot_vals$noise_vals))

# plot emmeans over raw data
hp120 <- df %>% 
  ggplot(aes(x=noise2frames_behav, y=zConf)) +
  theme_bw() + geom_hline(yintercept=0, linetype='dashed') + 
  scale_color_gradient2() + scale_fill_gradient2() + 
  geom_point(aes(color=signal1_cueEv), size=1.5, position=position_jitter(height=0.1)) + 
  # add emmeans
  geom_line(aes(xvar, yvar, color=signal1_cueEv, group=signal1_cueEv), emm_df, linewidth=0.5) +
  geom_pointrange(aes(xvar, yvar, ymin=LCL, ymax=UCL, color=signal1_cueEv), emm_df) + 
  labs(title = 'signal2 confidence', subtitle='noise2frames < 120')
```

```{r signal2conf: noise < 150, echo=F}
# filter data
df <- inferenceData_tidy %>% filter(catch_trial == 0, respPeriod == 'signal2', cueIdx < 3, noise2frames_behav < 150)

# fit model
hm150 <- lm(zConf ~ noise2frames_behav * signal1_cueEv, df)

# make vector for plotting emmeans
plot_vals <- df %>%
  select(noise2frames_behav, signal1_cueEv) %>%
  summarise(noise_vals = quantile(noise2frames_behav, probs = seq(0,1,0.1), na.rm=T, names=F),
            signal_vals = quantile(signal1_cueEv, probs = seq(0,1,0.1), na.rm=T, names=F))

# compute expected marginal means
emm <- emmeans(hm150, ~ noise2frames_behav | signal1_cueEv, 
               at = list(noise2frames_behav = plot_vals$noise_vals,
                         signal1_cueEv = plot_vals$signal_vals))

# save plot-formatted emmeans
emm_df <- emmip(hm150, ~ noise2frames_behav | signal1_cueEv, CIs=T, plotit=F,
                at = list(signal1_cueEv = plot_vals$signal_vals,
                          noise2frames_behav = plot_vals$noise_vals))

# plot emmeans over raw data
hp150 <- df %>% 
  ggplot(aes(x=noise2frames_behav, y=zConf)) +
  theme_bw() + geom_hline(yintercept=0, linetype='dashed') + 
  scale_color_gradient2() + scale_fill_gradient2() + 
  geom_point(aes(color=signal1_cueEv), size=1.5, position=position_jitter(height=0.1)) + 
  # add emmeans
  geom_line(aes(xvar, yvar, color=signal1_cueEv, group=signal1_cueEv), emm_df, linewidth=0.5) +
  geom_pointrange(aes(xvar, yvar, ymin=LCL, ymax=UCL, color=signal1_cueEv), emm_df) + 
  labs(title = 'signal2 confidence', subtitle='noise2frames < 150')
```

```{r display time-window results, echo=F, fig.width=12}

hp90 + hp120 + hp150 + hp + plot_layout(guides='collect', nrow=1)

tab_model(hm90, hm120, hm150, hm,
          dv.labels = c('noise2frames < 90',
                        'noise2frames < 120',
                        'noise2frames < 150', 
                        'all noise2frames'))

```

it does! the crossover for confidence ratings also seems to happen earlier than for choice probabilities: ~82 noise2frames vs. ~ 87. probably not a difference that makes a difference though
