---
title: "Pilot results - July 2024"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

## load libraries & data, tidy data
```{r setup, include=FALSE}
library(tidyverse)
library(patchwork)
library(wesanderson)

inferenceData_tidy <- read.csv('poster_data/inference_data.csv')
learningData_tidy <- read.csv('poster_data/learning_data.csv')
modelData <- read.csv('poster_data/0.52coh_10_thresh_confidence.csv')

inferenceData_tidy <- inferenceData_tidy %>% filter(pilotGroup == 'group2')
nSubs <- length(unique(inferenceData_tidy$subID))

modelData <- modelData %>%
  filter(is.na(noise1Frames)==F) %>%
  mutate(cue = factor(cue),
         threshold = factor(threshold),
         congruent = case_when(cue==0.8 & congruent==1 ~ 'congruent',
                               cue==0.8 & congruent==0 ~ 'incongruent',
                               cue==0.5 & congruent==1 ~ 'neutral',
                               cue==0.5 & congruent==0 ~ 'neutral'),
         congruent = factor(congruent, levels=c('incongruent', 'neutral', 'congruent')),
         accuracyFactor = factor(forcedChoice, levels=c(1,0), labels=c('correct', 'incorrect')))
outdir <- ('poster_plots/')
```


## accuracy: simulated / predicted
```{r}
individualSummary_model <- modelData %>%
  group_by(subID) %>%
  mutate(logRT = log(RT),
         zlogRT = scale(logRT)) %>%
  group_by(subID, congruent) %>%
  summarise(propCorrect_raw = mean(rawChoice, na.rm=T),
            propCorrect_forced = mean(forcedChoice),
            meanRT = mean(RT))

groupSummary_model <- modelData %>%
  group_by(congruent) %>%
  summarise(propCorrect_raw = mean(rawChoice, na.rm=T),
            propCorrect_forced = mean(forcedChoice),
            meanRT = mean(RT),
            raw_sem = sd(rawChoice, na.rm=T)/sqrt(9),
            forced_sem = sd(forcedChoice)/sqrt(9),
            RT_sem = sd(RT)/sqrt(9))

ggplot(groupSummary_model, aes(x=congruent, y=propCorrect_forced, color=congruent, fill=congruent)) +
  geom_hline(yintercept = 0.5, linewidth=0.15) +
  geom_col(position = position_dodge(width=0.9), width=0.75, fill='white', linewidth=2) +
  geom_errorbar(aes(ymin=propCorrect_forced - forced_sem, ymax=propCorrect_forced + forced_sem), width=0.1,
                position = position_dodge(width=0.9), color='gray25') +
  geom_point(data=individualSummary_model, position=position_jitterdodge(dodge.width=0.25, jitter.width = 0.15), 
             color='gray25', shape=21, size=2, alpha=0.7) +
  geom_point(size=2, color='gray25', position = position_dodge(width=0.25)) +
  labs(y = 'proportion correct', x='') + 
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_classic() +
  theme(legend.position = 'none',
        text = element_text(size=16),
        #axis.text.x = element_text(size=18),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=18),
        axis.text.x = element_blank())
ggsave(paste0(outdir, 'accuracy_model.png'), width=4.5, height=4, dpi='retina')
```

## accuracy: measured / observed
```{r accuracy summary, echo=FALSE, message=FALSE, warning=FALSE, out.width='60%'}
inferenceData_tidy <- inferenceData_tidy %>% 
  mutate(accuracyFactor=factor(accuracy, levels=c(1,0), labels=c('correct', 'incorrect')),
         congruent = factor(congruent, levels=c('incongruent', 'neutral', 'congruent')))

# compute accuracy within individuals
individualSummary <- inferenceData_tidy %>%
  group_by(subID, congruent) %>%
  summarise(propCorrect = mean(accuracy),
            meanRT = mean(zlogRT),
            meanZConf = mean(zConf))

# compute accuracy across individuals
groupSummary <- inferenceData_tidy %>%
  group_by(congruent) %>%
  summarise(propCorrect = mean(accuracy),
            accuracy_sem = sd(accuracy) / sqrt(nSubs),
            meanRT = mean(zlogRT),
            RT_sem = sd(zlogRT) / sqrt(nSubs),
            meanConf = mean(zConf),
            conf_sem = sd(zConf)/sqrt(nSubs)) 

# plot accuracy
ggplot(groupSummary, aes(x=congruent, y=propCorrect, fill=congruent)) +
  ylim(0,1) +
  geom_hline(yintercept=0.5, linewidth=0.15) +
  geom_col(position = position_dodge(width=0.25), width = 0.9) +
  geom_errorbar(aes(ymin=propCorrect - accuracy_sem, ymax = propCorrect + accuracy_sem), width=0.1,
                position = position_dodge(width=0.25), color='gray25') +
  geom_point(size=2, color='gray25',position = position_dodge(width=0.25)) +
  geom_point(data=individualSummary, position=position_jitterdodge(dodge.width=0.25, jitter.width = 0.15), 
             color='gray25', shape=21, size=2, alpha=0.7) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_classic() +
  labs(y = 'proportion correct') +
  theme(legend.position = 'none',
        text = element_text(size=16),
        #axis.text.x = element_text(size=18),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=18),
        axis.text.x = element_blank())
ggsave(paste0(outdir, 'accuracy.png'), width=4.5, height=4, dpi='retina')
```

takeaways:
* behavior follows predictions! 
* accuracy increases as a function of cue predictiveness 
* noise frames impair decision accuracy relative to noise-free flickers used during calibration -- accuracy is slightly above chance for neutral trials when theoretically it should be at the level of performance we calibrated to


## RT plot: simulated / predicted
```{r}
individualSummary_model <- modelData %>%
  group_by(subID, congruent, accuracyFactor) %>%
  summarise(meanRT = mean(RT))

groupSummary_model <- modelData %>%
  group_by(congruent, accuracyFactor) %>%
  summarise(meanRT = mean(RT),
            RT_sem = sd(RT)/sqrt(9))

ggplot(groupSummary_model, aes(x=congruent, y=meanRT, color=congruent, fill=congruent)) +
  facet_wrap(~ accuracyFactor) + 
  geom_col(position = position_dodge(width=0.9), width=0.9, fill='white', linewidth=2) +
  geom_errorbar(aes(ymin=meanRT - RT_sem, ymax=meanRT + RT_sem), width=0.1,
                position = position_dodge(width=0.9), color='gray25') +
  geom_point(data=individualSummary_model, position=position_jitterdodge(dodge.width=0.25, jitter.width = 0.15), 
             color='gray25', shape=21, size=2, alpha=0.7) +
  geom_point(size=2, color='gray25', position = position_dodge(width=0.25)) +
  labs(y='response time') +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_classic() +
  theme(legend.position = 'none',
        text = element_text(size=16),
        #axis.text.x = element_text(size=18),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=18),
        strip.text = element_text(size=22),
        axis.text.x = element_blank())
ggsave(paste0(outdir, 'RT_model.png'), width=7, height=4)
```

## RT plot: measured / observed
```{r RT, warning=FALSE, echo=FALSE, message=FALSE, out.width='60%'}
groupSummary <- inferenceData_tidy %>%
  mutate(accuracyFactor = factor(accuracy, levels=c(1,0), labels=c('correct', 'incorrect'))) %>%
  group_by(accuracyFactor, congruent) %>%
  summarise(meanRT = mean(zlogRT),
         RT_sem = sd(zlogRT) / sqrt(nSubs),
         meanConf = mean(zConf),
         conf_sem = sd(zConf) / sqrt(nSubs))

# then compute individual summaries
individualSummary <- inferenceData_tidy %>%
  group_by(accuracyFactor, congruent, subID) %>%
  summarise(meanRT = mean(zlogRT),
            meanConf = mean(zConf))

# plot accuracy * RT interaction
groupSummary %>%
ggplot(aes(x=congruent, y=meanRT, fill=congruent)) +
  facet_wrap(~accuracyFactor) +
  geom_hline(yintercept=0, linewidth=0.15) +
  geom_col(color='gray25') + 
  geom_errorbar(aes(ymin=meanRT - RT_sem, ymax = meanRT + RT_sem), width=0.1,
                color='gray25') +
  geom_point(data=individualSummary, position=position_jitterdodge(dodge.width=0.25, jitter.width = 0.25), 
             color='gray25', shape=21, size=2, alpha=0.9) +
  geom_point(size=2, color='gray25',position = position_dodge(width=0.25)) +
  labs(x='', y = 'response time') + 
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_classic() +
  theme(legend.position = 'none',
        text = element_text(size=16),
        #axis.text.x = element_text(size=18),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=18),
        strip.text = element_text(size=22),
        axis.text.x = element_blank())
ggsave(paste0(outdir, 'RT.png'), width=7, height=4)
```

takeaway:
* behavior largely follows predictions! one difference is that neutral is slightly slower in the human data, whereas the model predicts that incongruent should be the slowest. but the pattern that we see in the data makes sense to us --
* participants make correct responses faster when the cue is congruent with visual evidence
* participants make *in*correct responses faster when the cue is *in*congruent with visual evidence 


******************************************************************************

## confidence plot
```{r confidence, echo=FALSE, warning=FALSE, out.width='60%'}
groupSummary %>%
  ggplot(aes(x=congruent, y=meanConf, fill=congruent)) +
  theme_classic() + 
  facet_wrap(~accuracyFactor) +
  geom_hline(yintercept=0, linewidth=0.15) +
  geom_col(color='gray25') + 
  geom_errorbar(aes(ymin=meanConf - conf_sem, ymax = meanConf + conf_sem), width=0.1,
                color='gray25') +
  geom_point(size=2, color='gray25',position = position_dodge(width=0.25)) +
  geom_point(data=individualSummary, position=position_jitterdodge(dodge.width=0.25, jitter.width = 0.25), 
             color='gray25', shape=21, size=2, alpha=0.9) +
  labs(x='', y = 'decision confidence') + 
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  theme_classic() +
  theme(legend.position = 'none',
        text = element_text(size=16),
        #axis.text.x = element_text(size=18),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=18),
        strip.text = element_text(size=22),
        axis.text.x = element_blank())
ggsave(paste0(outdir, 'confidence.png'), width=7, height=4)
```

takeaway
* participants are more confident in their correct responses when the cue is congruent with visual evidence, and *less* confident in their incorrect responses when the cue is incongruent with visual evidence
* participants are less confident in their correct responses when the cue is incongruent with visual evidence, and more confident in their incorrect responses when the cue is incongruent with visual evidence 


## accumulator figure with noise periods
# load & tidy data
```{r}
library(tidyverse)
blue = 'dodgerblue1'
orange = 'darkorange1'
brown = 'saddlebrown'

# load in data
dynamic_congruent <- read.csv('../../presentations/noiseFrameData/dynamic_strong_congruent.csv', header = F) %>%
  rename(memory = V1, vision = V2, dv = V3) %>%
  mutate(time = 1:nrow(.))
dynamic_congruent_neutral <- read.csv('../../presentations/noiseFrameData/dynamic_neutral_congruent.csv', header = F) %>%
  rename(memory = V1, vision = V2, dv = V3) %>%
  mutate(time = 1:nrow(.))
dynamic_incongruent <- read.csv('../../presentations/noiseFrameData/dynamic_strong_incongruent.csv', header = F) %>%
  rename(memory = V1, vision = V2, dv = V3) %>%
  mutate(time = 1:nrow(.))
dynamic_incongruent_neutral <- read.csv('../../presentations/noiseFrameData/dynamic_neutral_incongruent.csv', header = F) %>%
  rename(memory = V1, vision = V2, dv = V3) %>%
  mutate(time = 1:nrow(.))
```

# plot congruent & incongruent traces
```{r}
# plot congruent
foo <- rnorm(1500)
dynamic_congruent %>%
  ggplot(aes(x=time)) + 
  ylim(-250, 250) + 
  xlim(0, 1500) +
  annotate('rect', xmin=0, xmax=350, ymin=-250, ymax=250, alpha=0.2, fill='gray') + 
  annotate('rect', xmin=730, xmax=730+500, ymin=-250, ymax=250, alpha=0.2, fill='gray') + 
  geom_hline(yintercept=c(0, 250),linewidth=c(0.25, 0.5)) + 
  geom_line(aes(y=vision), color=orange, linewidth=1) + 
  geom_line(aes(y=memory), color=blue,linetype='solid', linewidth=1) + 
  geom_line(data=dynamic_congruent_neutral, aes(y=memory), color=blue, linetype='dotted', linewidth=1) +
  geom_line(data=dynamic_congruent, aes(y=dv), color=brown, linewidth=1.25) +
  geom_line(data=dynamic_congruent_neutral, aes(y=dv), color=brown, linewidth=1.25, linetype='dotted') +
  geom_line(data=dynamic_incongruent, aes(y=cumsum(foo)*1), color=brown, linewidth=1.25, linetype='dashed') +
  theme_classic()  +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank())

ggsave(paste0(outdir,'congruentTrace.png'), width=4, height=3, dpi='retina')
ggsave(paste0(outdir,'bothTraces.png'), width=4, height=3, dpi='retina')

# plot incongruent
dynamic_incongruent %>%
  ggplot(aes(x=time)) + 
  ylim(-250, 250) + 
  annotate('rect', xmin=0, xmax=350, ymin=-250, ymax=250, alpha=0.2, fill='gray') + 
  annotate('rect', xmin=730, xmax=730+500, ymin=-250, ymax=250, alpha=0.2, fill='gray') + 
  geom_hline(yintercept=c(0, 250), linewidth=c(0.25, 0.5)) + 
  geom_line(aes(y=memory), color=blue, linewidth=1) + 
  geom_line(data=dynamic_incongruent_neutral, aes(y=memory), color=blue, linetype='dotted', linewidth=1) +
  geom_line(aes(y=vision),  color=orange, linewidth=1) + 
  geom_line(aes(y=dv),color=brown, linewidth=1.25) + 
  geom_line(data=dynamic_incongruent_neutral, aes(y=dv), size=0.75, color=brown, linetype='dotted', linewidth=1) + 
  theme_classic() + 
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank())
ggsave(paste0(outdir, 'incongruentTrace.png'), width=4, height=3, dpi='retina')
```



############### ari playground
## confidence simulation
```{r confidence, echo=FALSE, warning=FALSE, out.width='60%'}

df <- modelData %>% mutate(inverseConf = 1/accumulatorDifference)

df_group <- df %>%
  group_by(congruent, accuracyFactor) %>%
  summarise(confidence1 = mean(accumulatorDifference),
            confidence1_sem = sd(accumulatorDifference)/sqrt(9),
            confidence2 = mean(vizDifference),
            confidence2_sem = sd(vizDifference)/sqrt(9),
            confidence3 = mean(inverseConf),
            confidence3_sem = sd(inverseConf)/sqrt(9))

df_ind <- df %>%
  group_by(congruent, accuracyFactor, subID) %>%
  summarise(confidence1 = mean(accumulatorDifference),
            confidence2 = mean(vizDifference),
            confidence3 = mean(inverseConf))


## confidence as absolute difference in accumulator position
df_group %>%
  ggplot(aes(x=congruent, y=confidence1, fill=congruent,color=congruent)) +
  theme_classic() + 
  facet_wrap(~accuracyFactor) +
  geom_hline(yintercept=0, linewidth=0.15) +
  geom_col(fill='white',linewidth=2) + 
  geom_errorbar(aes(ymin=confidence1 - confidence1_sem, ymax = confidence1 + confidence1_sem), width=0.1,
                color='gray25') +
  geom_point(size=2, color='gray25',position = position_dodge(width=0.25)) +
  geom_point(data=df_ind, position=position_jitterdodge(dodge.width=0.25, jitter.width = 0.25), 
             color='gray25', shape=21, size=2, alpha=0.9) +
  labs(y = 'decision confidence', title='abs(memoryAccumulator(RT) - visionAccumulator(RT))') + 
  #scale_fill_brewer(palette = "Dark2") +
  #scale_color_brewer(palette = "Dark2") +
  theme_classic() +
  theme(legend.position = 'none',
        axis.title.x = element_blank())
ggsave('confidenceModel_absOnly.png', width=6)


## 
df_group %>%
  ggplot(aes(x=congruent, y=confidence3, fill=congruent,color=congruent)) +
  theme_classic() + 
  facet_wrap(~accuracyFactor) +
  geom_hline(yintercept=0, linewidth=0.15) +
  geom_col(fill='white',linewidth=2) + 
  geom_errorbar(aes(ymin=confidence3 - confidence3_sem, ymax = confidence3 + confidence3_sem), width=0.1,
                color='gray25') +
  geom_point(size=2, color='gray25',position = position_dodge(width=0.25)) +
  geom_point(data=df_ind, position=position_jitterdodge(dodge.width=0.25, jitter.width = 0.25), 
             color='gray25', shape=21, size=2, alpha=0.9) +
  labs(y = 'decision confidence', title='confidence as inverse difference') + 
  #scale_fill_brewer(palette = "Dark2") +
  #scale_color_brewer(palette = "Dark2") +
  theme_classic() +
  theme(legend.position = 'none',
        text = element_text(size=16),
        #axis.text.x = element_text(size=18),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=18),
        strip.text = element_text(size=22),
        axis.text.x = element_blank())

ggsave(paste0(outdir,'confidence_model.png'), width=7, height=4)
```


# can we get a confidence spike in the second noise period too??
```{r}
df <- df %>%
  mutate(respPeriod = case_when(RT <= noise1Frames ~ 1,
                                RT <= noise1Frames + signal1Frames ~ 2,
                                RT <= noise1Frames + signal1Frames + noise2Frames ~ 3,
                                RT > noise1Frames + signal1Frames + noise2Frames ~ 4))

df_group <- df %>%
  group_by(congruent, accuracyFactor, respPeriod) %>%
  summarise(confidence = mean(inverseConf),
            sem = sd(inverseConf,na.rm=T)/sqrt(9))


df_ind <- df %>%
  group_by(congruent, accuracyFactor, respPeriod, subID) %>%
  summarise(confidence = mean(inverseConf))

df_group %>%
  ggplot(aes(x=respPeriod, y=confidence, color=congruent, fill=congruent, alpha=congruent)) +
  geom_pointrange(aes(ymin=confidence - sem, ymax = confidence + sem)) +
  geom_line(aes(group=congruent, alpha=congruent)) +
  scale_alpha_manual(values=c(1, 0.5, 0.5)) +
  theme_classic() +
  labs(x='', y = 'confidence') +
  theme(legend.position = 'top') 
ggsave(paste0(outdir, 'confidenceSpike_model.png'), width=5, height=4)
```


#### trying to see if lowering threshold will give us the spike; from 10 -> 7
```{r}
df <- read.csv('poster_data/0.52coh_10_thresh_confidence.csv') %>%
  filter(is.na(noise1Frames)==F) %>%
  mutate(inverseConf = 1/accumulatorDifference,
         cue = factor(cue),
         threshold = factor(threshold),
         accuracyFactor = factor(forcedChoice, levels=c(1,0), labels=c('correct', 'incorrect')),
         congruent = case_when(cue==0.8 & congruent==1 ~ 'congruent',
                               cue==0.8 & congruent==0 ~ 'incongruent',
                               cue==0.5 & congruent==1 ~ 'neutral',
                               cue==0.5 & congruent==0 ~ 'neutral'),
         congruent = factor(congruent, levels=c('incongruent', 'neutral', 'congruent')),
         respPeriod = case_when(RT <= noise1Frames ~ 1,
                                RT <= noise1Frames + signal1Frames ~ 2,
                                RT <= noise1Frames + signal1Frames + noise2Frames ~ 3,
                                RT > noise1Frames + signal1Frames + noise2Frames ~ 4))

df_group <- df %>%
  group_by(congruent, respPeriod) %>%
  summarise(confidence = mean(inverseConf),
            sem = sd(inverseConf,na.rm=T)/sqrt(9),
            rt = mean(RT),
            rt_sem = sd(RT)/sqrt(9))


df_ind <- df %>%
  group_by(congruent, respPeriod, subID) %>%
  summarise(confidence = mean(inverseConf),
            rt = mean(RT))

df_group %>%
  ggplot(aes(x=respPeriod, y=confidence, color=congruent, fill=congruent, alpha=congruent)) +
  geom_pointrange(aes(ymin=confidence - sem, ymax = confidence + sem)) +
  geom_line(aes(group=congruent, alpha=congruent)) +
  scale_alpha_manual(values=c(1, 0.5, 0.5)) +
  theme_classic() +
  labs(x='', y = 'confidence') +
  theme(legend.position = 'top') 
ggsave(paste0(outdir, 'confidenceSpike_model.png'), width=5, height=4)
```

