---
title: "pilot analyses: setup & noise2 regressions"
output: 
  github_document:
    toc: true
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---


# LOAD & TIDY MODEL DATA FOR COMPARISONS
```{r}
model_df <- read.csv('steadyState_modelBehavior.csv')

# compute noise2frames_obs
signal2_model <- model_df %>% 
  filter(RT > noise2Onsets) %>%
  mutate(noise2frames_obs = case_when(RT < signal2Onsets ~ (noise2Onsets+noise2Frames) - RT,
                                      RT >= signal2Onsets ~ noise2Frames),
         congruent = case_when(cue==0.5 ~ 'neutral',
                               cue==0.8 & congruent==0 ~ 'incongruent',
                               cue==0.8 & congruent==1 ~ 'congruent'),
         congruent = factor(congruent, levels=c('incongruent', 'congruent', 'neutral')))
```


# ACCURACY
```{r display flicker accuracy across phases, echo=F, fig.dpi=300, fig.height=6, fig.width=8}

p1 <- calibration_df %>%
  group_by(subID, targetIdx) %>%
  summarise(propCorrect = mean(accuracy)) %>%
  ggplot(aes(x=targetIdx, y=propCorrect)) +
  theme_bw() +
  geom_hline(yintercept = 0.7) +
  geom_boxplot(varwidth=1) +
  geom_point(aes(color=subID), size=2, position=position_jitter(width=0.01, height=0)) +
  scale_color_manual(values=unname(cols25())) +
  #geom_line(aes(group=subID), alpha=0.15) +
  labs(title = 'calibration')

p2 <- cohVal_df %>%
  group_by(subID, targetIdx) %>%
  summarise(propCorrect = mean(accuracy)) %>%
  ggplot(aes(x=targetIdx, y=propCorrect)) +
  theme_bw() +
  geom_hline(yintercept = 0.7) +
  geom_boxplot(varwidth=1) +
  geom_point(aes(color=subID), size=2, position=position_jitter(width=0.01, height=0)) +
  scale_color_manual(values=unname(cols25())) +
  #geom_line(aes(group=subID), alpha=0.15) +
  labs(title = 'coherence validation')

p3 <- inference_df %>%
  group_by(subID, targetIdx) %>%
  summarise(propCorrect = mean(accuracy)) %>%
  ggplot(aes(x=targetIdx, y=propCorrect)) +
  theme_bw() +
  geom_hline(yintercept = 0.7) +
  geom_boxplot(varwidth=1) +
  geom_point(aes(color=subID), size=2, position=position_jitter(width=0.01, height=0)) +
  scale_color_manual(values=unname(cols25())) +
  #geom_line(aes(group=subID), alpha=0.15) +
  labs(title = 'inference')

p1 + p2 + p3 + plot_layout(guides = 'collect') & ylim(0.35, 1)

ggsave('accuracy_targetIdx.png')
```

#### broken down by image name
```{r display accuracy across phases by imageName, echo=F, fig.dpi=300, fig.height=6, fig.width=8}

p1 <- calibration_df %>%
  group_by(subID, targetImage) %>%
  summarise(propCorrect = mean(accuracy)) %>%
  ggplot(aes(x=targetImage, y=propCorrect)) +
  theme_bw() +
  geom_hline(yintercept = 0.7) +
  geom_boxplot(varwidth=1) +
  geom_point(aes(color=subID), size=2, position=position_jitter(width=0.01, height=0)) +
  scale_color_manual(values=unname(cols25())) +
  geom_line(aes(group=subID), alpha=0.15) +
  labs(title = 'calibration')

p2 <- cohVal_df %>%
  group_by(subID, targetName) %>%
  summarise(propCorrect = mean(accuracy)) %>%
  ggplot(aes(x=targetName, y=propCorrect)) +
  theme_bw() +
  geom_hline(yintercept = 0.7) +
  geom_boxplot(varwidth=1) +
  geom_point(aes(color=subID), size=2, position=position_jitter(width=0.01, height=0)) +
  scale_color_manual(values=unname(cols25())) +
  geom_line(aes(group=subID), alpha=0.15) +
  labs(title = 'coherence validation')

p3 <- inference_df %>%
  group_by(subID, targetName) %>%
  summarise(propCorrect = mean(accuracy)) %>%
  ggplot(aes(x=targetName, y=propCorrect)) +
  theme_bw() +
  geom_hline(yintercept = 0.7) +
  geom_boxplot(varwidth=1) +
  geom_point(aes(color=subID), size=2, position=position_jitter(width=0.01, height=0)) +
  scale_color_manual(values=unname(cols25())) +
  geom_line(aes(group=subID), alpha=0.15) +
  labs(title = 'inference')

p1 + p2 + p3 + plot_layout(guides = 'collect') & ylim(0.35, 1)

ggsave('accuracy_targetName.png')
```

### let's make the same plots for RTs
```{r display flicker accuracy across phases, echo=F, fig.dpi=300, fig.height=6, fig.width=8}

p1 <- calibration_df %>%
  group_by(subID, targetImage) %>%
  summarise(zRT = mean(zlogRT, na.rm=T)) %>%
  ggplot(aes(x=targetImage, y=zRT)) +
  theme_bw() +
  geom_hline(yintercept = 0) +
  geom_boxplot(varwidth=1) +
  geom_point(aes(color=subID), size=2, position=position_jitter(width=0.01, height=0)) +
  scale_color_manual(values=unname(cols25())) +
  geom_line(aes(group=subID), alpha=0.15) +
  labs(title = 'calibration')

p2 <- cohVal_df %>%
  group_by(subID, targetName) %>%
  summarise(zRT = mean(zlogRT, na.rm=T)) %>%
  ggplot(aes(x=targetName, y=zRT)) +
  theme_bw() +
  geom_hline(yintercept = 0) +
  geom_boxplot(varwidth=1) +
  geom_point(aes(color=subID), size=2, position=position_jitter(width=0.01, height=0)) +
  scale_color_manual(values=unname(cols25())) +
  geom_line(aes(group=subID), alpha=0.15) +
  labs(title = 'coherence validation')

p3 <- inference_df %>%
  group_by(subID, targetName) %>%
  summarise(zRT = mean(zlogRT, na.rm=T)) %>%
  ggplot(aes(x=targetName, y=zRT)) +
  theme_bw() +
  geom_hline(yintercept = 0) +
  geom_boxplot(varwidth=1) +
  geom_point(aes(color=subID), size=2, position=position_jitter(width=0.01, height=0)) +
  scale_color_manual(values=unname(cols25())) +
  geom_line(aes(group=subID), alpha=0.15) +
  labs(title = 'inference')

p1 + p2 + p3 + plot_layout(guides = 'collect')

ggsave('zlogRT_targetName.png')
```

### let's see how frequently each image is assigned to each targetIdx
```{r target assignment densities}

calibration_df %>%
  group_by(targetImage, targetIdx) %>%
  count() %>%
  ggplot(aes(x=targetIdx, y=n/40, color=targetImage, fill=targetImage)) +
  geom_col(position = 'dodge') + theme_bw() +
  labs(y = 'assignment frequency')

ggsave('image_assignment.png', width=7, height=4)
```

# CUE EFFECTS
```{r summary plots}

p1 <- inference_df %>%
  filter(catch_trial == 0) %>%
  mutate(trueCue = factor(trueCue)) %>%
  group_by(subID, trueCue, congruent) %>%
  summarise(propCorrect = mean(accuracy)) %>%
  ggplot(aes(x=congruent, y=propCorrect)) +
  theme_bw() + 
  geom_hline(yintercept = 0.7) + 
  geom_boxplot() +
  geom_point(aes(color=subID), size=2, position=position_jitter(width=0.01, height=0)) +
  scale_color_manual(values=unname(cols25())) +
  geom_line(aes(group=subID), alpha=0.15) + 
  labs(x='', title='inference accuracy')


p2 <- inference_df %>%
  filter(catch_trial == 0) %>%
  group_by(subID, trueCue, congruent) %>%
  summarise(RT = mean(zlogRT, na.rm=T)) %>%
  ggplot(aes(x=congruent, y=RT)) +
  theme_bw() + 
  geom_hline(yintercept = 0) + 
  geom_boxplot() +
  geom_point(aes(color=subID), size=2, position=position_jitter(width=0.01, height=0)) +
  scale_color_manual(values=unname(cols25())) +
  geom_line(aes(group=subID), alpha=0.15) + 
  labs(x='', title='inference RTs (zlogged)')

p1 + p2 + plot_layout(guides = 'collect')

ggsave('inferenceBehavior.png', width=10)
```

#### NOISE2 EFFECTS #### 
```{r noise2 regression setup}
signal2_behavior <- inference_test %>% 
  filter(respFrame >= noise2Onset_design)

plot_vals <- signal2_behavior %>% 
  select(noise2frames_obs, totalEv_signal1, totalEv_signal2) %>%
  summarise(noise_vals = quantile(noise2frames_obs, probs = seq(0,1,0.1), na.rm=T, names=F))
```

## accuracy of noise2 & signal 2 responses: behavior + model
```{r}

# fit human behavior
mb <- glm(accuracy ~ noise2frames_obs * congruent, signal2_behavior, family='binomial')

# plot emmeans
p1 <- mb %>%
  emmeans(., ~ noise2frames_obs | congruent, type='response', 
          at=list(noise2frames_obs=unique(signal2_behavior$noise2frames_obs))) %>% 
  as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_line() +
  geom_hline(yintercept = 0.5) +
  labs(y='p(correct)', title='behavior')

# plot slopes
p2 <- mb %>% 
  emtrends(., 'congruent', var='noise2frames_obs') %>%
  as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_obs.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')


# fit model forced choice
mf <- glm(forcedChoice ~ noise2frames_obs * congruent, signal2_model, family='binomial')

# plot emmeans
p3 <- mf %>%
  emmeans(., ~ noise2frames_obs | congruent, type='response', 
            at=list(noise2frames_obs=range())) %>%
  as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_hline(yintercept = 0.5) +
  geom_line() +
  labs(y='p(correct)', title='model: forced choice')

# plot slopes
p4 <- mf %>% 
  emtrends(., 'congruent', var='noise2frames_obs') %>%
  as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_obs.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')


# fit model raw choice
mr <- glm(rawChoice ~ noise2frames_obs * congruent, signal2_model, family='binomial')

# plot emmeans
p5 <- mr %>%
  emmeans(., ~ noise2frames_obs | congruent, type='response', 
            at=list(noise2frames_obs=plot_vals$noise_vals)) %>%
  as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_hline(yintercept = 0.5) +
  geom_line() +
  labs(y='p(correct)', title='model: raw choice')

# plot slopes
p6 <- mr %>% 
  emtrends(., 'congruent', var='noise2frames_obs') %>%
  as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_obs.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')


(p1 + p2) / (p3 + p4) / (p5 + p6) + plot_annotation(title = 'NOISE2 & SIGNAL2: correct response ~ noise2frames_obs * congruent')
ggsave('v4_figures_round2/accuracy_noise2signal2.png', height=8, width=8)
```

### accuracy of noise2 responses only: behavior + model
```{r}

p1 <- signal2_behavior %>%
  filter(respFrame < signal2Onset_design) %>%
  glm(accuracy ~ noise2frames_obs * congruent, ., family='binomial') %>%
    emmeans(., ~ noise2frames_obs | congruent, type='response', at=list(noise2frames_obs=plot_vals$noise_vals)) %>%
  as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_line() +
  labs(y='p(correct)', title='noise2 responses only')

p2 <- signal2_behavior %>%
  filter(respFrame < signal2Onset_design) %>%
  glm(accuracy ~ noise2frames_obs * congruent, ., family='binomial') %>%
  emtrends(., 'congruent', var='noise2frames_obs')  %>%
  as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_obs.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')


p3 <- signal2_model %>% 
  filter(RT < signal2Onsets) %>%
  glm(forcedChoice ~ noise2frames_obs * congruent, ., family='binomial') %>%
  emmeans(., ~ noise2frames_obs | congruent, type='response', 
          at=list(noise2frames_obs=plot_vals$noise_vals)) %>%
  as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_line() +
  labs(y='p(correct)', title='model')

p4 <- signal2_model %>% 
  filter(RT < signal2Onsets) %>%
  glm(forcedChoice ~ noise2frames_obs * congruent, ., family='binomial') %>%
  emtrends(., 'congruent', var='noise2frames_obs') %>%
  as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_obs.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')

p1 + p2 + p3 + p4 + plot_annotation(title = 'correct response ~ noise2frames_obs * congruent')
ggsave('v4_figures_round2/accuracy_noise2Only.png', height=6, width=8)
```

### accuracy of signal2 responses only: behavior + model
```{r}
p1 <- signal2_behavior %>%
  filter(respFrame >= signal2Onset_design) %>%
  glm(accuracy ~ noise2frames_obs * congruent, ., family='binomial') %>%
    emmeans(., ~ noise2frames_obs | congruent, type='response', at=list(noise2frames_obs=plot_vals$noise_vals)) %>%
  as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_line() +
  labs(y='p(correct)', title='signal2 responses only')

p2 <- signal2_behavior %>%
  filter(respFrame >= signal2Onset_design) %>%
  glm(accuracy ~ noise2frames_obs * congruent, ., family='binomial') %>%
  emtrends(., 'congruent', var='noise2frames_obs')  %>%
  as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_obs.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')


p3 <- signal2_model %>% 
  filter(RT >= signal2Onsets) %>%
  glm(forcedChoice ~ noise2frames_obs * congruent, ., family='binomial') %>%
  emmeans(., ~ noise2frames_obs | congruent, type='response', 
          at=list(noise2frames_obs=plot_vals$noise_vals)) %>%
  as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_line() +
  labs(y='p(correct)', title='model')

p4 <- signal2_model %>% 
  filter(RT >= signal2Onsets) %>%
  glm(forcedChoice ~ noise2frames_obs * congruent, ., family='binomial') %>%
  emtrends(., 'congruent', var='noise2frames_obs') %>%
  as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_obs.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')

p1 + p2 + p3 + p4 + plot_annotation(title = 'correct response ~ noise2frames_obs * congruent')
ggsave('v4_figures_round2/accuracy_signal2Only.png', height=6, width=8)
```

# NOISE2 EFFECTS - CUECONGCHOICE
```{r}
# human behavior
cueCong_emm <- glm(cueCongResponse_obj ~ noise2frames_obs * congruent, signal2_behavior, family='binomial') %>%
    emmeans(., ~ noise2frames_obs | congruent, type='response', at=list(noise2frames_obs=plot_vals$noise_vals))

cueCong_trends <- glm(cueCongResponse_obj ~ noise2frames_obs * congruent, signal2_behavior, family='binomial') %>% 
  emtrends(., 'congruent', var='noise2frames_obs') 

p1 <- cueCong_emm %>% as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_hline(yintercept=0.5) +
  geom_line() +
  labs(y='p(chooseCue)', title='cueCongChoice ~ noise2frames * congruent')

p2 <- cueCong_trends %>% as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_obs.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')

p1 + p2 & theme(axis.text = element_text(size=12))

ggsave('chooseCue_noise2_obs*cong.png', width=10, height=4)

#### model predictions
signal2_model <- signal2_model %>%
  mutate(cueCongResponse = case_when(congruent=='congruent' & forcedChoice==1 ~ 1,
                                     congruent=='incongruent' & forcedChoice==0 ~ 1,
                                     congruent=='congruent' & forcedChoice==0 ~ 0,
                                     congruent=='incongruent' & forcedChoice==1 ~ 0))


cueCong_emm <- glm(cueCongResponse ~ noise2frames_obs * congruent, signal2_model, family='binomial') %>%
    emmeans(., ~ noise2frames_obs | congruent, type='response', 
            at=list(noise2frames_obs = quantile(signal2_model$noise2frames_obs, probs = seq(0,1,0.1), na.rm=T, names=F)))

cueCong_trends <- glm(cueCongResponse ~ noise2frames_obs * congruent, signal2_model, family='binomial') %>% 
  emtrends(., 'congruent', var='noise2frames_obs') 

p1 <- cueCong_emm %>% as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_hline(yintercept=0.5) +
  geom_line() +
  labs(y='p(chooseCue)', title='cueCongChoice ~ noise2frames * congruent')

p2 <- cueCong_trends %>% as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_obs.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')

p1 + p2 & theme(axis.text = element_text(size=12))

ggsave('chooseCue_noise2_obs*cong_model.png', width=10, height=4)


## on the same timescale of noise2obs as humans
cueCong_emm <- glm(cueCongResponse ~ noise2frames_obs * congruent, signal2_model, family='binomial') %>%
    emmeans(., ~ noise2frames_obs | congruent, type='response', 
            at=list(noise2frames_obs = plot_vals$noise_vals))

cueCong_trends <- glm(cueCongResponse ~ noise2frames_obs * congruent, signal2_model, family='binomial') %>% 
  emtrends(., 'congruent', var='noise2frames_obs') 

p1 <- cueCong_emm %>% as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_hline(yintercept=0.5) +
  geom_line() +
  labs(y='p(chooseCue)', title='cueCongChoice ~ noise2frames * congruent')

p2 <- cueCong_trends %>% as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_obs.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')

p1 + p2 & theme(axis.text = element_text(size=12))

ggsave('chooseCue_noise2_obs*cong_modelAbridged.png', width=10, height=4)
```

# NOISE 2 EFFECTS - RT
```{r}

rt_emm <- signal2_behavior %>%
  filter(respFrame > signal2Onset_design) %>%
  mutate(sig2locked_RT = respFrame - signal2Onset_design) %>%
  lm(sig2locked_RT ~ noise2frames_obs * congruent, .) %>%
  emmeans(., ~ noise2frames_obs | congruent, at=list(noise2frames_obs=plot_vals$noise_vals))

rt_trends <- signal2_behavior %>%
  filter(respFrame > signal2Onset_design) %>%
  mutate(sig2locked_RT = respFrame - signal2Onset_design) %>%
  lm(sig2locked_RT ~ noise2frames_obs * congruent, .) %>%
  emtrends(., 'congruent', var='noise2frames_obs')

p1 <- rt_emm %>% as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=emmean, color=congruent, fill=congruent)) +
  theme_bw() + 
  geom_pointrange(aes(ymin=lower.CL, ymax=upper.CL)) +
  geom_line() +
  labs(y='respFrame - signal2Onset', title='sig2locked_respFrame ~ noise2frames * congruent')

p2 <- rt_trends %>% as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_obs.trend, ymin=lower.CL, ymax=upper.CL, color=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')

p1 + p2 
ggsave('rt_noise2_obs*cong.png', width=10, height=4)

## adding decision accuracy as a predictor
rt_emm <- signal2_behavior %>%
  filter(respFrame > signal2Onset_design) %>%
  mutate(sig2locked_RT = respFrame - signal2Onset_design) %>%
  lm(sig2locked_RT ~ noise2frames_obs * congruent * accuracyFactor, .) %>%
  emmeans(., ~ noise2frames_obs | congruent*accuracyFactor, at=list(noise2frames_obs=plot_vals$noise_vals))

rt_emm %>% as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=emmean, color=congruent, fill=congruent)) +
  theme_bw() + 
  geom_pointrange(aes(ymin=lower.CL, ymax=upper.CL)) +
  geom_line() +
  facet_wrap(~accuracyFactor) +
  labs(y='respFrame - signal2Onset', title='sig2locked_respFrame ~ noise2frames * congruent * accuracy')

ggsave('rt_noise2_obs*cong*accuracy.png', width=10, height=4)

###### model predictions
rt_emm <- signal2_model %>%
  filter(RT > signal2Onsets) %>%
  mutate(sig2locked_RT = RT - signal2Onsets) %>%
  lm(sig2locked_RT ~ noise2frames_obs * congruent, .) %>%
  emmeans(., ~ noise2frames_obs | congruent, at=list(noise2frames_obs=plot_vals$noise_vals))

rt_trends <- signal2_model %>%
  filter(RT > signal2Onsets) %>%
  mutate(sig2locked_RT = RT - signal2Onsets) %>%
  lm(sig2locked_RT ~ noise2frames_obs * congruent, .) %>%
  emtrends(., 'congruent', var='noise2frames_obs')

p1 <- rt_emm %>% as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=emmean, color=congruent, fill=congruent)) +
  theme_bw() + 
  geom_pointrange(aes(ymin=lower.CL, ymax=upper.CL), shape=5) +
  geom_line() +
  labs(y='respFrame - signal2Onset', title='sig2locked_respFrame ~ noise2frames * congruent')

p2 <- rt_trends %>% as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_obs.trend, ymin=lower.CL, ymax=upper.CL, color=congruent)) +
  theme_bw() +
  geom_pointrange(shape=5) +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')

p1 + p2 
ggsave('rt_noise2_obs*cong_model.png', width=10, height=4)


#### accuracy interaction
rt_emm <- signal2_model %>%
  filter(RT > signal2Onsets) %>%
  mutate(sig2locked_RT = RT - signal2Onsets) %>%
  lm(sig2locked_RT ~ noise2frames_obs * congruent * forcedChoice, .) %>%
  emmeans(., ~ noise2frames_obs | congruent*forcedChoice, at=list(noise2frames_obs=plot_vals$noise_vals))

rt_emm %>% as.data.frame() %>%
  ggplot(aes(x=noise2frames_obs, y=emmean, color=congruent, fill=congruent)) +
  theme_bw() + 
  geom_pointrange(aes(ymin=lower.CL, ymax=upper.CL), shape=5) +
  geom_line() +
  facet_wrap(~forcedChoice) +
  labs(y='respFrame - signal2Onset', title='sig2locked_respFrame ~ noise2frames * congruent * accuracy')

ggsave('rt_noise2_obs*cong*accuracy_model.png', width=10, height=4)
```

# EFFECTS OF NOISE1 ON SIGNAL 1 CHOICE BIASES
```{r}

# cueCong response
cueCong_emm <- inference_test %>%
  filter(respFrame < noise2Onset_design) %>%
  glm(cueCongResponse_obj ~ noise1frames_obs * congruent, ., family='binomial') %>%
    emmeans(., ~ noise1frames_obs | congruent, type='response', at=list(noise1frames_obs=plot_vals$noise_vals))

cueCong_trends <- inference_test %>%
  filter(respFrame < noise2Onset_design) %>%
  glm(cueCongResponse_obj ~ noise1frames_obs * congruent, ., family='binomial') %>% 
  emtrends(., 'congruent', var='noise1frames_obs') 

p1 <- cueCong_emm %>% as.data.frame() %>%
  ggplot(aes(x=noise1frames_obs, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_hline(yintercept=0.5) +
  geom_line() +
  labs(y='p(chooseCue)', title='cueCongChoice ~ noise1frames * congruent')

p2 <- cueCong_trends %>% as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise1frames_obs.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise1 effect') +
  theme(legend.position = 'none')

p1 + p2 & theme(axis.text = element_text(size=12))

ggsave('chooseCue_noise1_obs*cong.png', width=10, height=4)
```


# NOISE RESPONDING DATA
```{r responses in noise 1 & noise 2}

# proportion of noise1 responses 
p1 <- inference_test %>%
  mutate(noise1resp = ifelse(respFrame < signal1Onset_design, 1, 0),
         noise1cue = ifelse(congruent=='neutral', '50%', '80%')) %>%
  group_by(noise1cue, subID) %>%
  summarise(noise1resp = mean(noise1resp)) %>%
  ggplot(aes(x=noise1cue, y=noise1resp)) +
  theme_bw() +
  geom_line(aes(group=subID), alpha=0.25, color='gray') +
  geom_point(aes(color=subID)) +
  scale_color_manual(values=c(unname(cols25()[1:13]), '#F8766D', '#619CFF')) +
  stat_summary(aes(color=noise1cue), fun.data = 'mean_se', position = position_dodge2(width=3)) +
  labs(y='', title='proportion of responses made during first noise') +
  theme(legend.position='none')

p2 <- inference_test %>%
  mutate(noise1resp = ifelse(respFrame < signal1Onset_design, 1, 0),
         noise1cue = ifelse(congruent=='neutral', '50%', '80%')) %>%
  ggplot(aes(x=sig1locked_rt/60, color=noise1cue, fill=noise1cue)) +
  theme_bw() +
  geom_histogram(alpha=0.5, bins=50) +
  geom_vline(xintercept=0) +
  labs(title = 'RT locked to onset of signal1', x='RT (seconds)')

# proportion of noise2 responses
p3 <- inference_test %>%
  mutate(noise2resp = ifelse(respFrame < signal2Onset_design & respFrame > noise2Onset_design, 1, 0)) %>%
  group_by(congruent, subID) %>%
  summarise(noise2resp = mean(noise2resp)) %>%
  ggplot(aes(x=congruent, y=noise2resp, color=subID)) +
  theme_bw() +
  geom_line(aes(group=subID), alpha=0.25, color='gray') +
  geom_point() +
  scale_color_manual(values=c(unname(cols25()[1:13]), "#F8766D", "#00BA38", "#619CFF")) +
  stat_summary(aes(color=congruent), fun.data = 'mean_se', position = position_dodge2(width=6)) +
  labs(y='', title='proportion of responses made during second noise', x='')

p4 <- inference_test %>%
  mutate(sig2locked_rt = (respFrame - signal2Onset_design)/60) %>%
  ggplot(aes(x=sig2locked_rt, color=congruent, fill=congruent)) +
  theme_bw() +
  geom_histogram(alpha=0.5, bins=50) +
  geom_vline(xintercept=0) +
  labs(title = 'RT locked to onset of signal2', x='RT (seconds)')
  
p1 + p2 + p3 + p4 + plot_layout(guides = 'collect')
ggsave('noiseResponseSummary.png', height=8, width=10)
```

# NOISE 1 EFFECTS
```{r}

plot_vals <- inference_test %>% 
  select(noise1frames_design) %>%
  summarise(noise_vals = quantile(noise1frames_design, probs = seq(0,1,0.1), na.rm=T, names=F))

#### accuracy #### 
acc_emm <- glm(accuracy ~ noise1frames_design * congruent, inference_test, family='binomial') %>%
    emmeans(., ~ noise1frames_design | congruent, type='response', at=list(noise1frames_design=plot_vals$noise_vals))

acc_trends <- glm(accuracy ~ noise1frames_design * congruent, inference_test, family='binomial') %>% 
  emtrends(., 'congruent', var='noise1frames_design') 

p1 <- acc_emm %>% as.data.frame() %>%
  ggplot(aes(x=noise1frames_design, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_line() +
  labs(y='p(correct)', title='correct response ~ noise1frames * congruent')

p2 <- acc_trends %>% as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise1frames_design.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise1 effect') +
  theme(legend.position = 'none')

p1 + p2 & theme(axis.text = element_text(size=12))

ggsave('acc_noise1*cong.png', width=10, height=4)

rt_emm <- lm(sig1locked_rt ~ noise1frames_design * congruent, inference_test) %>%
  emmeans(., ~ noise1frames_design | congruent, at=list(noise1frames_design=plot_vals$noise_vals))

rt_trends <- lm(sig1locked_rt ~ noise1frames_design * congruent, inference_test) %>%
  emtrends(., 'congruent', var='noise1frames_design')

p1 <- rt_emm %>% as.data.frame() %>%
  ggplot(aes(x=noise1frames_design, y=emmean, color=congruent, fill=congruent)) +
  theme_bw() + 
  geom_hline(yintercept = 0) +
  geom_pointrange(aes(ymin=lower.CL, ymax=upper.CL)) +
  geom_line() +
  labs(y='zlogRT', title='zlogRT ~ noise1frames * congruent')

p2 <- rt_trends %>% as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_design.trend, ymin=lower.CL, ymax=upper.CL, color=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')

p1 + p2 & theme(axis.text = element_text(size=12))
ggsave('rt_noise2*cong.png', width=10, height=4)

# cueCong response
cueCong_emm <- glm(cueCongResponse_obj ~ noise2frames_design * congruent, signal2_behavior, family='binomial') %>%
    emmeans(., ~ noise2frames_design | congruent, type='response', at=list(noise2frames_design=plot_vals$noise_vals))

cueCong_trends <- glm(cueCongResponse_obj ~ noise2frames_design * congruent, signal2_behavior, family='binomial') %>% 
  emtrends(., 'congruent', var='noise2frames_design') 

p1 <- cueCong_emm %>% as.data.frame() %>%
  ggplot(aes(x=noise2frames_design, y=prob, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent, fill=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_hline(yintercept=0.5) +
  geom_line() +
  labs(y='p(chooseCue)', title='cueCongChoice ~ noise2frames * congruent')

p2 <- cueCong_trends %>% as.data.frame() %>%
  ggplot(aes(x=congruent, y=noise2frames_design.trend, ymin=asymp.LCL, ymax=asymp.UCL, 
             color=congruent)) +
  theme_bw() +
  geom_pointrange() +
  geom_hline(yintercept = 0) +
  labs(x='', title='slope of noise2 effect') +
  theme(legend.position = 'none')

p1 + p2 & theme(axis.text = element_text(size=12))

ggsave('chooseCue_noise2*cong.png', width=10, height=4)
```
```