---
title: "Pilot analyses: version 3"
output: 
  github_document:
    toc: true
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---

hello! if you are looking for the source code to produce the results displayed below, you should navigate to the `.Rmd` version of this document.

# model specs
model data come from a simulation of 100 subjects performing the task. each simulated subject completes 100 trials for the 80% cue and 50 trials for the 50% cue. RTs were log-transformed and z-scored within subject. all choice data is forced choice (i.e., sign of the accumulator at trial end if a boundary hadn't been reached). 

simulations were run with coherence=0.5395, thinning=12, and threshold=5. coherence & threshold values were determined in a separate "model calibration" analysis linked in my notebook. this combination led to the model performing at 70% accuracy based on visual evidence only without any noise durations, just forward & backward masking of each signal frame with noise

# data tidying

```{r load packages, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
library(tidyverse)
library(patchwork)
library(lme4)
library(lmerTest)
library(emmeans)

# potentially useful in the future
# library(performance) # for easy model comparisons
# library(jtools) # for alternative model summaries
# library(sjPlot) # for formatting model result tables
# library(MetBrewer) # for pretty art-inspired color palettes
```

```{r plotting setup: colors, outdir, functions, include=F}
# define plotting colors 
colors <- c('incongruent' = "#F8766D", 'neutral' = "#00BA38", 'congruent'="#619CFF")
trialCong_cols <- c('incongruent' = "#F8766D", 'equal evidence' = "lemonchiffon3", 'congruent'="#619CFF")
cueType_cols <- c('50%' = 'gray', '80%' = 'darkblue')
blues <- RColorBrewer::brewer.pal(9, "Blues")[c(4,5,6,7,8)]
cueCong_colors <- c('0.8 cue: incongruent vizEv' = "#F8766D", 
            '0.8 cue: equal vizEv' = "#00BA38", 
            '0.8 cue: congruent vizEv'="#619CFF",
            '0.5 cue: imgA vizEv' = 'purple',
            '0.5 cue: imgB vizEv' = 'orange',
            '0.5 cue: equal vizEv' = '#00BA38')

# where to save plots
outdir <- 'pilot_analysis_figs/'

# function for plotting effects of continuous predictors
varRange <- function(df, xVar, precision=1) {
  return(seq(min(df[,xVar], na.rm=T),
             max(df[,xVar], na.rm=T),
             precision))
}
```

```{r load & tidy inference data, include=FALSE}
evidence_frames <- read.csv('../data/tidied/evidenceFrames.csv')  %>% rename(respFrame = response_frame)
inference_files = list.files('../data', full.names = TRUE, pattern='block1_inference.csv', recursive = TRUE)
inference_keep_idx <- grep('excluded', inference_files, invert=T)
inference_df = do.call(rbind, lapply(inference_files[inference_keep_idx], function(x) { read.csv(x, header = TRUE)} )) 

############### tidy inference data ############### 
inferenceData <- inference_df %>%
  filter(subID != 16) %>%
  rename(trueTarget = targetIdx) %>% 
  select(-c(noise1frames, noise2frames, signal1frames, block, targetImg, cue_rgb, cue_string)) %>%
  full_join(., evidence_frames, by=c('subID', 'trial', 'catch_trial', 'congruent', 'respFrame', 'response')) %>%
  mutate(subID = factor(subID),
         congruent = factor(as.character(congruent), levels=c("0", "NaN", "1"), labels=c('incongruent', 'neutral', 'congruent')),
         respFrame = ifelse(is.na(respFrame), 540, respFrame),
         cueIdx = case_when(trueTarget == 1 & congruent == 'congruent' ~ 1,
                            trueTarget == 1 & congruent == 'incongruent' ~ 2,
                            trueTarget == 1 & congruent == 'incongruent' ~ 2,
                            trueTarget == 2 & congruent =='congruent' ~ 2,
                            trueTarget == 2 & congruent=='incongruent' ~ 1,
                            congruent == 'neutral' ~ 3),
         cueType = ifelse(cueIdx==3, '50% cue', '80% cue'),
         totalNoise = noise1frames_behav + noise2frames_behav,
         totalTarget1 = rowSums(across(c(signal1_target1, signal2_target1)), na.rm=T),
         totalTarget2 = rowSums(across(c(signal1_target2, signal2_target2)), na.rm=T),
         trialTarget = case_when(totalTarget1 > totalTarget2 ~ 1,
                                 totalTarget1 < totalTarget2 ~ 2,
                                 totalTarget1 == totalTarget2 ~ NA),
         # trialCongruence = case_when(cueIdx == trialTarget ~ 'congruent',
         #                             cueIdx != trialTarget ~ 'incongruent',
         #                             totalTarget1 == totalTarget2 ~ 'equal evidence'),
         # trialCongruence = factor(trialCongruence, levels=c('incongruent', 'equal evidence', 'congruent')),
         respPeriod = case_when(respFrame >= signal2Onset ~ 'signal2', 
                                respFrame >= noise2Onset & respFrame < signal2Onset ~ 'noise2',
                                respFrame > noise1frames_design & respFrame < noise2Onset ~ 'signal1',
                                respFrame < signal1Onset ~ 'noise1'), 
         cueCongChoice = case_when(cueIdx==3 ~ NA, cueIdx==response ~ 1, cueIdx!=response ~ 0),
         noise1_quartile = cut(noise1frames_behav, breaks=quantile(noise1frames_behav, na.rm=T), include.lowest = T, labels=F), 
         noise2_quartile = cut(noise2frames_behav, breaks=quantile(noise2frames_behav, na.rm=T), include.lowest = T, labels=F), 
         totalNoise_quartile = cut(totalNoise, breaks=quantile(totalNoise, na.rm=T), include.lowest = T, labels=F),
         catch_trial_cat = factor(catch_trial, levels=c(0,1), labels=c('test', 'catch'))) %>%
  group_by(subID) %>%
  mutate(logRT = log(RT),
         zlogRT = scale(logRT),
         zConf = scale(confResp),
         logConfRT = log(confRT),
         zlogconfRT = scale(logConfRT), 
         rt_quartile = cut(zlogRT, breaks=quantile(zlogRT, na.rm=T), include.lowest=T, labels=F),
         trial_quartile = cut(trial, breaks=quantile(trial), include.lowest=T, labels=F)) %>%
  ungroup()

rm(inference_files, inference_keep_idx, evidence_frames, inference_df)
```

```{r load & tidy model data, include=FALSE}
modelData <- read.csv('steadyState_modelBehavior.csv')

modelData <- modelData %>%
  mutate(congruent = case_when(cue==0.5 ~ NA,
                               congruent==0 ~ 'incongruent',
                               congruent==1 ~ 'congruent'),
         noise1frames_behav = case_when(RT > noise1Frames ~ noise1Frames,
                                         RT < noise1Frames ~ RT),
         noise2frames_behav = case_when(RT > signal2Onsets ~ noise2Frames,
                                         RT < signal2Onsets & RT > noise2Onsets ~ signal2Onsets - RT),
         signal1frames_behav = case_when(RT > signal1Onsets + signal1Frames ~ signal1Frames,
                                         RT < signal1Onsets + signal1Frames ~ noise2Onsets - RT),
         signal2frames_behav = case_when(RT < signal2Onsets ~ NA,
                                         RT > signal2Onsets ~ (signal2Onsets+signal2Frames)-RT),
         respPeriod = case_when(RT >= signal2Onsets ~ 'signal2', 
                                RT >= noise2Onsets & RT < signal2Onsets ~ 'noise2',
                                RT > noise1Frames & RT < noise2Onsets ~ 'signal1',
                                RT < signal1Onsets ~ 'noise1'),
         cueCongChoice = case_when(congruent == 'congruent' & forcedChoice == 1 ~ 1,
                                   congruent == 'incongruent' & forcedChoice == 1 ~ 1),
         noise1_quartile = cut(noise1frames_behav, breaks=quantile(noise1frames_behav, na.rm=T), include.lowest = T, labels=F), 
         noise2_quartile = cut(noise2frames_behav, breaks=quantile(noise2frames_behav, na.rm=T), include.lowest = T, labels=F)) %>% 
  group_by(subID) %>%
  mutate(logRT = log(RT),
         zlogRT = scale(logRT)) %>%
  ungroup()
```

```{r make dfs for analysis}
inferenceData_tidy <- inferenceData %>%
  filter(is.na(response)==F) %>%
  mutate(cueType = factor(cueType),
         subID = factor(subID),
         resp1 = ifelse(response==1, 1, 0),
         resp2 = ifelse(response==1, 0, 1),
         respFinger = ifelse(resp1==1, '1', '2'),
         signal1_cueEv = case_when(cueIdx==1 ~ signal1_target1 - signal1_target2,
                                   cueIdx==2 ~ signal1_target2 - signal1_target1),
         # signal1_relEv = case_when(response==1 ~ signal1_target1 - signal1_target2,
         #                           response==2 ~ signal1_target2 - signal1_target1),
         # signal1_relEv_z = scale(signal1_relEv),
         # signal1_cueCong = case_when(cueIdx==1 & (signal1_target1 > signal1_target2) ~ '0.8 cue: congruent vizEv',
         #                             cueIdx==1 & (signal1_target1 < signal1_target2) ~ '0.8 cue: incongruent vizEv',
         #                             cueIdx==2 & (signal1_target1 > signal1_target2) ~ '0.8 cue: incongruent vizEv',
         #                             cueIdx==2 & (signal1_target1 < signal1_target2) ~ '0.8 cue: congruent vizEv',
         #                             cueIdx<3 & (signal1_target1 == signal1_target2) ~ '0.8 cue: equal vizEv',
         #                             cueIdx==3 & (signal1_target1 > signal1_target2) ~ '0.5 cue: imgA vizEv',
         #                             cueIdx==3 & (signal1_target1 < signal1_target2) ~ '0.5 cue: imgB vizEv',
         #                             cueIdx==3 & (signal1_target1 == signal1_target2) ~ '0.5 cue: equal vizEv'),
         # signal1_evCongChoice = case_when(signal1_target1 > signal1_target2 & response==1 ~ 1,
         #                                  signal1_target1 < signal1_target2 & response==2 ~ 1,
         #                                  signal1_target1 < signal1_target2 & response==1 ~ 0,
         #                                  signal1_target1 > signal1_target2 & response==2 ~ 0),
         # signal2_cueCong = case_when(cueIdx==1 & (signal2_target1 > signal2_target2) ~ '0.8 cue: congruent vizEv',
         #                             cueIdx==1 & (signal2_target1 < signal2_target2) ~ '0.8 cue: incongruent vizEv',
         #                             cueIdx==2 & (signal2_target1 > signal2_target2) ~ '0.8 cue: incongruent vizEv',
         #                             cueIdx==2 & (signal2_target1 < signal2_target2) ~ '0.8 cue: congruent vizEv',
         #                             cueIdx<3 & (signal2_target1 == signal2_target2) ~ '0.8 cue: equal vizEv',
         #                             cueIdx==3 & (signal2_target1 > signal2_target2) ~ '0.5 cue: imgA ev',
         #                             cueIdx==3 & (signal2_target1 < signal2_target2) ~ '0.5 cue: imgB ev',
         #                             cueIdx==3 & (signal2_target1 == signal2_target2) ~ '0.5 cue: equal ev'),
         # signal2_cueCong = factor(signal2_cueCong),
         # signal1_cueCong = factor(signal1_cueCong),
         noise1_seconds = noise1frames_behav * (1/60), 
         signal1RT = RT - noise1_seconds,
         vizLocked_respFrame = respFrame - noise1frames_behav,
         vizLocked_respFrame_t = vizLocked_respFrame / 60,
         vizLocked_sig2Resp = respFrame - (noise1frames_behav + signal1frames_behav + noise2frames_behav),
         vizLocked_sig2Resp = vizLocked_sig2Resp/60) %>% 
  group_by(subID) %>%
  mutate(zlog_sig1RT = log(signal1RT),
         zlog_sig1RT = scale(zlog_sig1RT))%>%
  ungroup()

modelData <- modelData %>% 
  mutate(cueType = factor(cue, levels=c(0.5, 0.8), labels=c('50% cue', '80% cue')),
         subID = factor(subID),
         noise1_seconds = noise1frames_behav * (1/60), 
         vizLocked_respFrame = RT - noise1frames_behav,
         vizLocked_respFrame_t = vizLocked_respFrame / 60,
         vizLocked_sig2Resp = RT - (noise1frames_behav + signal1frames_behav + noise2frames_behav),
         vizLocked_sig2Resp = vizLocked_sig2Resp/60) 
```

# RT analyses

## effect of cue type on RT across all test trials
### human data
```{r zlogRT ~ cueType: humans, echo=F}
# run model
m <- inferenceData_tidy %>%
  filter(catch_trial == 0) %>%
  lm(zlogRT ~ cueType, ., contrasts=list(cueType=contr.sum))

# compute expected marginal means
emm <- emmeans(m, eff ~ cueType)

# quick plot
# emmip(m,  ~ cueType, CIs=T, plotit=T) + 
#   theme_bw() +  geom_hline(yintercept=0, linetype='dashed')

# save plot-formatted emmeans
emm_df <- emmip(m,  ~ cueType, CIs=T, plotit=F)

# plot emmeans above raw data
inferenceData_tidy %>%
  filter(catch_trial == 0) %>%
  ggplot(aes(x = cueType, y = zlogRT)) +
  theme_bw() + 
  geom_hline(yintercept=0, linetype='dashed') +
  geom_point(aes(color=cueType), alpha=0.1, color='gray50', position=position_jitter(width=0.1)) +
  # add emmeans
  geom_errorbar(aes(x=xvar, y=yvar, ymin=LCL, ymax=UCL, color=cueType), data=emm_df, width=0.05, size=1) +
  labs(title = 'marginal means over raw data')

summary(m)
```

### model data
```{r zlogRT ~ cueType: model, echo=F}
# fit linear model
m <- modelData %>%
  lm(zlogRT ~ cueType, ., contrasts=list(cueType=contr.sum))

# compute expected marginal means
emm <- emmeans(m, eff ~ cueType)

# quick plot
# emmip(m,  ~ cueType, CIs=T, plotit=T) + 
#   theme_bw() +  geom_hline(yintercept=0, linetype='dashed')

# save plot-formatted emmeans
emm_df <- emmip(m,  ~ cueType, CIs=T, plotit=F)

# plot emmeans above raw data
modelData %>%
  ggplot(aes(x = cueType, y = zlogRT)) +
  theme_bw() + 
  geom_hline(yintercept=0, linetype='dashed') +
  geom_point(aes(color=cueType), alpha=0.1, color='gray50', position=position_jitter(width=0.1)) +
  # add emmeans
  geom_errorbar(aes(x=xvar, y=yvar, ymin=LCL, ymax=UCL, color=cueType), data=emm_df, width=0.05, size=1) +
  labs(title = 'marginal means over raw data: model')

summary(m)
```

## effect of noise1 duration + cueType on RT for responses made after noise1
### human data
```{r zlogRT ~ noise1frames + cueType, echo=F}

# run model
m <- inferenceData_tidy %>%
  filter(catch_trial == 0) %>%
  filter(respPeriod != 'noise1') %>%
  lm(vizLocked_respFrame_t ~ noise1frames_behav * cueType, ., contrasts = list(cueType = contr.sum))

# compute expected marginal means
emm <- emmeans(m, consec ~ noise1frames_behav | cueType, cov.reduce=quantile)

# get range of x-values for plotting
noise_vals <- unique(summary(emm)$emmeans$noise1frames_behav)

# quick plot
#emmip(m,  ~ noise1frames_behav | cueType, cov.reduce=quantile, CIs=T, plotit=T)

# save plot-formatted emmeans
emm_df <- emmip(m,  ~ noise1frames_behav | cueType, CIs=T, plotit=F, cov.reduce=F)

# plot emmeans above raw data
inferenceData_tidy %>%
  filter(catch_trial == 0) %>%
  filter(respPeriod != 'noise1', noise1frames_behav >= min(noise_vals)) %>%
  ggplot(aes(x = noise1frames_behav, y = vizLocked_respFrame_t)) +
  theme_bw() +
  geom_point(aes(color=cueType), alpha=0.5, size=1) +
  geom_ribbon(aes(xvar, yvar, ymin=LCL, ymax=UCL, fill=cueType), emm_df, color=NA, alpha=0.5) +
  geom_line(aes(x=xvar, y=yvar, group=cueType), data=emm_df) +
  labs(title = 'effect of cue type & noise1 duration on RTs',
       subtitle = 'RT locked to onset of signal1 evidence, plotted on the scale of seconds')

summary(m)
# emmeans(m, consec ~ noise1frames_behav | cueType, cov.reduce=range)$contrasts
emtrends(m, pairwise ~ cueType, var='noise1frames_behav')
```


### model data
```{r zlogRT ~ noise1frames + cueType: model, echo=F}

# run model
m <- modelData %>%
  filter(respPeriod != 'noise1') %>%
  lm(vizLocked_respFrame_t ~ noise1frames_behav * cueType, ., contrasts = list(cueType = contr.sum))

# compute expected marginal means
emm <- emmeans(m, consec ~ noise1frames_behav | cueType, cov.reduce=quantile)

# get range of x-values for plotting
noise_vals <- unique(summary(emm)$emmeans$noise1frames_behav)

# quick plot
#emmip(m,  ~ noise1frames_behav | cueType, cov.reduce=quantile, CIs=T, plotit=T)

# save plot-formatted emmeans
emm_df <- emmip(m,  ~ noise1frames_behav | cueType, CIs=T, plotit=F, cov.reduce=F)

# plot emmeans above raw data
modelData %>%
  filter(respPeriod != 'noise1', noise1frames_behav >= min(noise_vals)) %>%
  ggplot(aes(x = noise1frames_behav, y = vizLocked_respFrame_t)) +
  theme_bw() +
  geom_point(aes(color=cueType), alpha=0.5, size=0.5) +
  geom_ribbon(aes(xvar, yvar, ymin=LCL, ymax=UCL, fill=cueType), emm_df, color=NA, alpha=0.5) +
  geom_line(aes(x=xvar, y=yvar, group=cueType), data=emm_df) +
  labs(title = 'effect of cue type & noise1 duration on RTs: model',
       subtitle = 'RT locked to onset of signal1 evidence, plotted on the scale of seconds')

summary(m)
# emmeans(m, consec ~ noise1frames_behav | cueType, cov.reduce=range)$contrasts
emtrends(m, consec ~ cueType, var='noise1frames_behav')
```

## effect of noise2 duration + cueType on zlogRT in signal2 
### human data
```{r vizLocked_sig2Resp ~ noise2frames_behav + cueType: humans, echo=F}
# fit model
m <- inferenceData_tidy %>%
  filter(catch_trial == 0) %>%
  filter(respPeriod == 'signal2') %>%
  lm(vizLocked_sig2Resp ~ noise2frames_behav * cueType, ., contrasts = list(cueType = contr.sum))

# compute expected marginal means
emm <- emmeans(m, consec ~ noise2frames_behav | cueType, cov.reduce=quantile)

# get range of x-values for plotting
noise_vals <- unique(summary(emm)$emmeans$noise2frames_behav)

# quick plot
# emmip(m,  ~ noise2frames_behav | cueType, cov.reduce=quantile, CIs=T, plotit=T)

# save plot-formatted emmeans
emm_df <- emmip(m,  ~ noise2frames_behav | cueType, CIs=T, plotit=F,
                at=list(noise2frames_behav = noise_vals))

# plot emmeans above raw data
inferenceData_tidy %>%
  filter(catch_trial == 0) %>%
  filter(respPeriod == 'signal2') %>%
  filter(noise2frames_behav >= min(noise_vals)) %>%
  ggplot(aes(x = noise2frames_behav, y = vizLocked_sig2Resp)) +
  theme_bw() +
  geom_point(aes(color=cueType), alpha=0.5, size=1) +
  geom_ribbon(aes(xvar, yvar, ymin=LCL, ymax=UCL, fill=cueType), emm_df, color=NA, alpha=0.5) +
  geom_line(aes(x=xvar, y=yvar, group=cueType, color=cueType), data=emm_df, linewidth=1.5) +
  labs(title = 'signal2 RTs locked to onset of signal2 visual evidence')

summary(m)
# print(emm)
#emmeans(m, pairwise ~ cueType | noise2frames_behav, cov.reduce=range)$contrasts
emtrends(m, pairwise ~ cueType, var='noise2frames_behav')
```

## effect of noise2 duration + cueType on zlogRT in signal2 
### model data
```{r vizLocked_sig2Resp ~ noise2frames_behav + cueType: model, echo=F}
# fit model
m <- modelData %>%
  filter(respPeriod == 'signal2') %>%
  lm(vizLocked_sig2Resp ~ noise2frames_behav * cueType, ., contrasts = list(cueType = contr.sum))

# compute expected marginal means
emm <- emmeans(m, consec ~ noise2frames_behav | cueType, cov.reduce=quantile)

# get range of x-values for plotting
noise_vals <- unique(summary(emm)$emmeans$noise2frames_behav)

# quick plot
# emmip(m,  ~ noise2frames_behav | cueType, cov.reduce=quantile, CIs=T, plotit=T)

# save plot-formatted emmeans
emm_df <- emmip(m,  ~ noise2frames_behav | cueType, CIs=T, plotit=F,
                at=list(noise2frames_behav = noise_vals))

# plot emmeans above raw data
modelData %>%
  filter(respPeriod == 'signal2') %>%
  filter(noise2frames_behav >= min(noise_vals)) %>%
  ggplot(aes(x = noise2frames_behav, y = vizLocked_sig2Resp)) +
  theme_bw() +
  geom_point(aes(color=cueType), alpha=0.5, size=1) +
  geom_ribbon(aes(xvar, yvar, ymin=LCL, ymax=UCL, fill=cueType), emm_df, color=NA, alpha=0.5) +
  geom_line(aes(x=xvar, y=yvar, group=cueType), data=emm_df) +
  labs(title = 'signal2 RTs locked to onset of signal2 visual evidence')

summary(m)
#print(emm)
emtrends(m, pairwise ~ cueType, var='noise2frames_behav')
```

# Response probability analyses

## for noise 1 responses only, probability of making cue-based response as a function of noise1 duration
### human data
```{r cueCongChoice_signal1 ~ noise1frames_behav: humans, echo=F}

# filter data & fit model
m <- inferenceData_tidy %>%
  filter(catch_trial == 0) %>%
  filter(respPeriod == 'noise1') %>%
  glm(cueCongChoice ~ noise1frames_behav, ., family='binomial')

# compute expected marginal means
emm <- emmeans(m, consec ~ noise1frames_behav, type='response', cov.reduce=range)

# get noise values from emmeans call
noise_vals <- unique(summary(emm)$emmeans$noise1frames_behav)

# quick plot
#emmip(m, ~ noise1frames_behav, type='response', CIs=T, at=list(noise1frames_behav=noise_vals))

# save plot-formatted emmeans
emm_df <- emmip(m,  ~ noise1frames_behav, type='response', CIs=T, plotit=F, at=list(noise1frames_behav=noise_vals))

# plot emmeans above raw data
inferenceData_tidy %>%
  filter(catch_trial == 0) %>%
  filter(respPeriod == 'noise1') %>%
  ggplot(aes(x = noise1frames_behav, y = cueCongChoice)) +
  theme_bw() + 
  geom_hline(yintercept=0.5, linetype='dashed') +
  geom_point(position=position_jitter(height=0.05)) +
  # add emmeans
  geom_ribbon(aes(x=xvar, y=yvar, ymin=LCL, ymax=UCL), data=emm_df, alpha=0.1) +
  geom_line(aes(x=xvar, y=yvar), data=emm_df) +
  labs(title = 'in noise1, probability of responding according to cue (80% cues only)')

summary(m)
print(emm)
```

### model data
```{r cueCongChoice_signal1 ~ noise1frames_behav: model, echo=F}

# filter data & fit model
m <- modelData %>%
  filter(respPeriod == 'noise1', cue==0.8) %>%
  glm(forcedChoice ~ noise1frames_behav, ., family='binomial')

# compute expected marginal means
emm <- emmeans(m, consec ~ noise1frames_behav, type='response', cov.reduce=range)

# get noise values from emmeans call
noise_vals <- unique(summary(emm)$emmeans$noise1frames_behav)

# quick plot
#emmip(m, ~ noise1frames_behav, type='response', CIs=T, at=list(noise1frames_behav=noise_vals))

# save plot-formatted emmeans
emm_df <- emmip(m,  ~ noise1frames_behav, type='response', CIs=T, plotit=F, at=list(noise1frames_behav=noise_vals))

# plot emmeans above raw data
modelData %>%
  filter(respPeriod == 'noise1', cue==0.8) %>%
  ggplot(aes(x = noise1frames_behav, y = forcedChoice)) +
  theme_bw() + 
  geom_hline(yintercept=0.5, linetype='dashed') +
  geom_point(position=position_jitter(height=0.05)) +
  # add emmeans
  geom_ribbon(aes(x=xvar, y=yvar, ymin=LCL, ymax=UCL), data=emm_df, alpha=0.1) +
  geom_line(aes(x=xvar, y=yvar), data=emm_df) +
  labs(title = 'in noise1, probability of responding according to cue (80% cues only)')

summary(m)
print(emm)
```


## For signal 2 responses only, probability of making cue-based response as a function of noise2 duration
### human data
```{r cueCongChoice_signal2 ~ noise2frames_behav: humans, echo=F}
# filter data & fit model
m <- inferenceData_tidy %>%
  filter(catch_trial == 0) %>%
  filter(respPeriod == 'signal2') %>%
  glm(cueCongChoice ~ noise2frames_behav, ., family='binomial')

# compute expected marginal means
emm <- emmeans(m, consec ~ noise2frames_behav, type='response', cov.reduce=range)

# get noise values from emmeans call
noise_vals <- unique(summary(emm)$emmean$noise2frames_behav)

# quick plot
# emmip(m, ~ noise2frames_behav, type='response', at=list(noise2frames_behav=noise_vals),
#       CIs=T, cov.reduce=F)

# save plot-formatted emmeans
emm_df <- emmip(m, ~ noise2frames_behav, type='response', at=list(noise2frames_behav=noise_vals),
                CIs=T, plotit=F, cov.reduce=F)

# plot emmeans above raw data
 inferenceData_tidy %>%
  filter(catch_trial == 0) %>%
  filter(respPeriod == 'signal2') %>% 
  ggplot(aes(x = noise2frames_behav, y = cueCongChoice)) +
  theme_bw() +
  geom_hline(yintercept=0.5, linetype='dashed') +
  geom_point(position=position_jitter(height=0.05), size=1) +
  # add emmeans
  geom_ribbon(aes(x=xvar, y=yvar, ymin=LCL, ymax=UCL), data=emm_df, alpha=0.1) +
  geom_line(aes(x=xvar, y=yvar), data=emm_df) +
  labs(title = 'probability of making cueCongruent signal2 response as a function of noise2 duration (80% cues only)')

summary(m)
print(emm)
```

### model data
```{r cueCongChoice_signal2 ~ noise2frames_behav: model, echo=F}
# filter data & fit model
m <- modelData %>%
  filter(respPeriod == 'signal2', cue==0.8) %>%
  glm(forcedChoice ~ noise2frames_behav, ., family='binomial')

# compute expected marginal means
emm <- emmeans(m, consec ~ noise2frames_behav, type='response', cov.reduce=range)

# get noise values from emmeans call
noise_vals <- unique(summary(emm)$emmean$noise2frames_behav)

# quick plot
# emmip(m, ~ noise2frames_behav, type='response', at=list(noise2frames_behav=noise_vals),
#       CIs=T, cov.reduce=F)

# save plot-formatted emmeans
emm_df <- emmip(m, ~ noise2frames_behav, type='response', at=list(noise2frames_behav=noise_vals),
                CIs=T, plotit=F, cov.reduce=F)

# plot emmeans above raw data
 modelData %>%
  filter(respPeriod == 'signal2', cue==0.8) %>% 
  ggplot(aes(x = noise2frames_behav, y = forcedChoice)) +
  theme_bw() +
  geom_hline(yintercept=0.5, linetype='dashed') +
  geom_point(position=position_jitter(height=0.05), size=1) +
  # add emmeans
  geom_ribbon(aes(x=xvar, y=yvar, ymin=LCL, ymax=UCL), data=emm_df, alpha=0.1) +
  geom_line(aes(x=xvar, y=yvar), data=emm_df) +
  labs(title = 'probability of making cueCongruent signal2 response as a function of noise2 duration (80% cues only)')

summary(m)
print(emm)
```

## Effect of signal1 evidence + noise2 duration on choice probabilities in signal2: 80% cues
### human data
```{r cueCongChoice_signal2 ~ noise2frames_behav * signal1Ev - continuous color: human, echo=F}
# fit model
m <- inferenceData_tidy %>%
    filter(catch_trial==0) %>%
    filter(respPeriod == 'signal2', cueIdx < 3) %>%
    # fit model
    glm(cueCongChoice ~ noise2frames_behav * signal1_cueEv, ., family = 'binomial')

# compute expected marginal means
emm <- emmeans(m, ~ noise2frames_behav | signal1_cueEv, type='response', cov.reduce=F)

# get predictor values from emmeans call
noise_vals <- unique(summary(emm)$noise2frames_behav)
signal_vals <- unique(summary(emm)$signal1_cueEv)

# quick plot
# emmip(m, signal1_cueEv ~ noise2frames_behav, type='response', CIs=T,
#       at = list(signal1_cueEv = signal_vals,
#                 noise2frames_behav = noise_vals))

# save plot-formatted emmeans
emm_df <- emmip(m, signal1_cueEv ~ noise2frames_behav, type='response', CIs=T, plotit=F,
                at = list(signal1_cueEv = signal_vals,
                          noise2frames_behav = noise_vals)) %>%
  mutate(signal1_cueEv = as.numeric(signal1_cueEv))

# plot emmeans over raw data
inferenceData_tidy %>%
  filter(catch_trial == 0, respPeriod=='signal2', cueIdx < 3) %>%
  ggplot(aes(x=noise2frames_behav, y=cueCongChoice)) +
  theme_bw() + geom_hline(yintercept=0.5, linetype='dashed') + 
  scale_color_gradient2() + scale_fill_gradient2() + 
  geom_point(aes(color=signal1_cueEv), size=1.5, position=position_jitter(height=0.1)) + 
  # add emmeans
  geom_line(aes(xvar, yvar, color=signal1_cueEv, group=signal1_cueEv), emm_df, linewidth=0.5) +
  labs(title = 'Probability of making a cue-congruent choice as a function of signal1 evidence & noise 2 duration')

emmeans(m, eff ~ noise2frames_behav | signal1_cueEv, type='response', cov.reduce=range)
```

### model data
```{r cueCongChoice_signal2 ~ noise2frames_behav * signal1Ev - continuous color: model, echo=F}
# filter data
m <- modelData %>%
    filter(respPeriod == 'signal2', cue==0.8) %>% 
    # fit model
    glm(forcedChoice ~ noise2frames_behav * signal1_vizEv, ., family = 'binomial')

# compute expected marginal means
emm <- emmeans(m, ~ noise2frames_behav | signal1_vizEv, type='response', cov.reduce=range)

# save plot-formatted emmeans
m_df <- modelData %>% filter(respPeriod == 'signal2', cue==0.8)
emm_df <- emmip(m, signal1_vizEv ~ noise2frames_behav, type='response', CIs=T, plotit=F,
                at = list(signal1_vizEv = varRange(m_df, 'signal1_vizEv', 5),
                          noise2frames_behav = varRange(m_df, 'noise2frames_behav', 5))) %>%
  mutate(signal1_vizEv = as.numeric(signal1_vizEv))

# plot emmeans over raw data
modelData %>%
  filter(respPeriod=='signal2', cue == 0.8) %>%
  ggplot(aes(x=noise2frames_behav, y=forcedChoice)) +
  theme_bw() + geom_hline(yintercept=0.5, linetype='dashed') + 
  scale_color_gradient2() + scale_fill_gradient2() + 
  geom_point(aes(color=signal1_vizEv), size=1.5, position=position_jitter(height=0.1)) + 
  # add emmeans
  geom_line(aes(xvar, yvar, color=signal1_vizEv, group=signal1_vizEv), emm_df, linewidth=0.5) +
  labs(title = 'Probability of making a cue-congruent choice as a function of signal1 evidence & noise 2 duration')

emmeans(m, eff ~ noise2frames_behav | signal1_vizEv, type='response', cov.reduce=range)
```


